\documentclass[a4paper,11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{geometry}
\geometry{left=1.5cm,right=1.5cm,top=1.2cm,bottom=1.5cm}

\usepackage{lmodern}
\usepackage{xcolor}

\definecolor{lyon_red}{RGB}{186, 12, 47}
\definecolor{LYON_RED}{RGB}{186, 12, 47}

\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    urlcolor=lyon_red,
    linkcolor=lyon_red,
    citecolor=lyon_red,
    pdfborder={0 0 0}
}

\usepackage{titlesec}
\usepackage{enumitem}

\pagestyle{empty}

\titleformat{\section}
  {\color{lyon_red}\Large\bfseries\uppercase}{}{0em}{}
  [\color{lyon_red}\titlerule]

\titlespacing\section{0pt}{10pt}{5pt}
\setlist[itemize]{leftmargin=*,topsep=2pt,itemsep=1pt}

\begin{document}

\begin{center}
    {\Huge\bfseries\color{lyon_red} AISSAOUI Ismail}\\[4pt]
    {\Large AI \& Computer Vision Engineer | PhD Candidate}\\[6pt]

    {\normalsize
    Email: \href{mailto:ismail.aissaoui.pro@gmail.com}{ismail.aissaoui.pro@gmail.com} \quad
    Phone: +213 660 70 77 96 \\
    Portfolio: \href{https://ismail-aissaoui.vercel.app}{ismail-aissaoui.vercel.app} \quad
    Location: Algeria (Relocation Ready) \\
    LinkedIn: \href{https://linkedin.com/in/aissaoui-ismail-6a77a92a7}{linkedin.com/in/aissaoui-ismail-6a77a92a7} \quad
    GitHub: \href{https://github.com/i-aissaoui}{github.com/i-aissaoui}
    }
\end{center}

%===========================
\section{PROFILE}
AI \& Computer Vision Engineer specialized in **Facial Recognition**, **Video Representation Learning**, and **Temporal Dynamics**. Expert in building robust vision pipelines with PyTorch and OpenCV. Proven ability to implement state-of-the-art architectures (ViT, Mamba-SSM) for complex sequential data. Deeply committed to the application of AI in Healthcare and Social Science (ASD Support).

%===========================
\section{EDUCATION}
\textbf{National Higher School of Computer Science (ESI-SBA)} \hfill 2021--2026 \\
\textbf{Engineering \& Master’s Degree in Artificial Intelligence} \\
\textit{Master's Thesis: "Modeling Temporal Dynamics for Industrial Systems using SSMs and xLSTM"} \\
Focus: Sequential Representation Learning, Domain Generalization, Real-time Inference.

%===========================
\section{TECHNICAL SKILLS}
\textbf{Computer Vision}: Facial Expression Recognition (FER), Image Processing, Object Detection (YOLOv8), Tracking (ByteTrack), Patch-based Attention (ViT). \\
\textbf{AI \& ML}: PyTorch, TensorFlow, OpenCV, State-Space Models (Mamba), Transformer Architectures, Domain Generalization, Self-Supervised Learning. \\
\textbf{Tools \& Infrastructure}: Git, Linux, Docker, CUDA, C++ JIT, InfluxDB, PostgreSQL. \\
\textbf{Web}: FastAPI, Next.js, WebSockets (for real-time vision streaming).

%===========================
\section{PROJECT HIGHLIGHTS}

\textbf{Recognizini — Real-Time Facial Recognition System} \hfill 2025 \\
\textit{LIRIS Focus: FER, Embeddings, Real-time Processing}
\begin{itemize}
    \item Developed an end-to-end facial recognition application featuring real-time identification and an active feedback loop for incremental embedding updates.
    \item Optimized facial feature extraction pipelines to handle varying head poses and illumination conditions.
\end{itemize}

\textbf{Vision Transformer (ViT) Implementation} \hfill 2025 \\
\textit{LIRIS Focus: Foundation Models, Attention Mechanisms}
\begin{itemize}
    \item Implemented the seminal Vision Transformer architecture from scratch in PyTorch, focusing on linear projection of image patches and multi-head self-attention.
\end{itemize}

\textbf{Industrial Temporal Modeling (Master's Thesis)} \hfill 2025--2026 \\
\textit{LIRIS Focus: Video Representation, Synchrony, SSMs}
\begin{itemize}
    \item Applied **Mamba-SSM** and **xLSTM** to model long-range temporal dependencies in high-frequency sensor data.
    \item Engineered models for **Domain Generalization**, enabling transfer between different fleet units with 98\% reliability.
\end{itemize}

\textbf{Real-time Safety \& Traffic Analytics (YOLOv8)} \hfill 2025 \\
\textit{LIRIS Focus: Monitoring, unconstrained scenes, OpenCV}
\begin{itemize}
    \item Built real-time monitoring systems for PPE compliance and traffic flow, utilizing ByteTrack for consistent object tracking across frames.
\end{itemize}

%===========================
\section{LANGUAGES}
English: Fluent (C1) \quad|\quad French: Fluent (C1) \quad|\quad Arabic: Native
\end{document}
