\documentclass[a4paper,11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{geometry}
\geometry{left=1.5cm,right=1.5cm,top=1.2cm,bottom=1.2cm}

\usepackage{lmodern}
\usepackage{xcolor}
\definecolor{titleblue}{RGB}{0,51,140}
\definecolor{TITLEBLUE}{RGB}{0,51,140}

\usepackage{hyperref}
\hypersetup{colorlinks=true, urlcolor=titleblue, linkcolor=titleblue}

\usepackage{titlesec}
\usepackage{enumitem}

\pagestyle{empty}

\titleformat{\section}{\color{titleblue}\Large\bfseries\uppercase}{}{0em}{}[\color{titleblue}\titlerule]
\titlespacing\section{0pt}{8pt}{4pt}
\setlist[itemize]{leftmargin=*,topsep=1pt,itemsep=1pt}

\begin{document}

\begin{center}
    {\Huge\bfseries\color{titleblue} AISSAOUI Ismail}\\[4pt]
    {\Large State Engineer in Artificial Intelligence \& Data Science}\\[6pt]
    ismail.aissaoui.pro@gmail.com $|$ +213 660 70 77 96 $|$ Algeria \\
    \href{https://linkedin.com/in/aissaoui-ismail-6a77a92a7}{linkedin.com/in/aissaoui-ismail-6a77a92a7} $|$ \href{https://github.com/i-aissaoui}{github.com/i-aissaoui}
\end{center}

\section{PROFESSIONAL SUMMARY}
State Engineer graduated from ESI-SBA, specializing in \textbf{Digital Twins}, 3D visualization, and real-time AI. Expert in "Edge-to-User" latency optimization and distributed architectures for Cyber-Physical Systems (CPS). PhD candidate focused on semantic data compression for industrial Extended Reality (XR).

\section{EDUCATION}
\textbf{National School of Computer Science (ESI-SBA, Algeria)} \hfill 2021 -- 2026 \\
\textbf{State Engineer's Degree \& MSc in Artificial Intelligence}

\section{WORK EXPERIENCE}
\textbf{AI Engineer Intern — 3D Digital Twin & Edge Computing} \hfill Jan 2026 -- Present \\
\textbf{Sonatrach (Pipeline Transport Branch)} \\
\begin{itemize}
    \item Designed an interactive 3D monitoring dashboard (\textbf{Unity/Three.js context}).
    \item Optimized inference latency to \textbf{0.04ms} using \textbf{C++ JIT Compiled xLSTM}.
    \item Developed generative surrogates (\textbf{Mamba-SSM}) for real-time industrial simulators.
    \item Hardware-Software Co-design for resource-constrained mobile devices.
\end{itemize}

\textbf{Network Engineering Intern} \hfill Sep 2024 \\
\textbf{Algérie Télécom RMC Center}

\section{RESEARCH & ENGINEERING PROJECTS}

\textbf{Geo-RAG — Geospatial Knowledge \& Reasoning} \hfill 2025 \\
Intelligent system using RAG for semantic multi-source data processing.
\textit{Key skill: Semantic analysis and knowledge extraction.}

\textbf{Recognizini — Real-Time Face Recognition \& CV} \hfill 2025 \\
Active learning system with incremental embeddings for high-speed computer vision.

\textbf{Career Connect — GNN recruitment Intelligence} \hfill 2024 -- 2025 \\
Modeling complex relationships using Graph Neural Networks (GNN).

\textbf{University Scheduling (NP-Complete Optimization)} \hfill 2025 \\
Complex system optimization using hybrid metaheuristics (\textbf{PSO/ACO/GA}).

\textbf{Aura — Reinforcement Learning \& Distributed Systems} \hfill 2025 \\
Distributed platform with real-time dashboards and autonomous agents.

\section{TECHNICAL SKILLS}
\begin{itemize}
    \item \textbf{XR \& Graphics}: Unity 3D, Three.js, Electron, 3D Data Visualization.
    \item \textbf{Real-Time AI}: Mamba-SSM, xLSTM, Edge Inference (C++), Latency Optimization.
    \item \textbf{Data Science}: Semantic Learning, Data Compression, GNN, PINN, RL.
    \item \textbf{Stack}: Python (PyTorch), C++, Docker, Node.js, Git, Linux.
\end{itemize}

\section{LANGUES}
Arabic (Native), English (Advanced), French (Fluent).

\end{document}
