\documentclass[a4paper,11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{geometry}
\geometry{left=1.5cm,right=1.5cm,top=1.2cm,bottom=1.5cm}

\usepackage{lmodern}
\usepackage{xcolor}

\definecolor{bosch_red}{RGB}{224, 0, 0}
\definecolor{BOSCH_RED}{RGB}{224, 0, 0}
\definecolor{darkgrey}{RGB}{64, 64, 64}

\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    urlcolor=bosch_red,
    linkcolor=bosch_red,
    citecolor=bosch_red,
    pdfborder={0 0 0}
}

\usepackage{titlesec}
\usepackage{enumitem}

\pagestyle{empty}

\titleformat{\section}
  {\color{bosch_red}\Large\bfseries\uppercase}{}{0em}{}
  [\color{bosch_red}\titlerule]

\titlespacing\section{0pt}{10pt}{5pt}
\setlist[itemize]{leftmargin=*,topsep=2pt,itemsep=1pt}

\begin{document}

\begin{center}
    {\Huge\bfseries\color{bosch_red} AISSAOUI Ismail}\\[4pt]
    {\Large AI \& Data Science Engineer | PhD Candidate}\\[6pt]

    {\normalsize
    Email: \href{mailto:ismail.aissaoui.pro@gmail.com}{ismail.aissaoui.pro@gmail.com} \quad
    Phone: +213 660 70 77 96 \\
    Portfolio: \href{https://ismail-aissaoui.vercel.app}{ismail-aissaoui.vercel.app} \quad
    Location: Algeria (Relocation Ready) \\
    LinkedIn: \href{https://linkedin.com/in/aissaoui-ismail-6a77a92a7}{linkedin.com/in/aissaoui-ismail-6a77a92a7} \quad
    GitHub: \href{https://github.com/i-aissaoui}{github.com/i-aissaoui}
    }
\end{center}

%===========================
\section{PROFILE}
AI \& Data Science Engineer specialized in **General Purpose AI (GPAI)**, **System 1/2** sequential reasoning, and **Industrial World Models**. Expert in bridging high-fidelity physics with deep learning (Mamba-SSM, PINNs) for real-time edge applications. Proven track record in achieving sub-millisecond inference for safety-critical industrial systems. Eager to advance Smart Manufacturing through GPAI-driven robotics.

%===========================
\section{EDUCATION}
\textbf{National Higher School of Computer Science (ESI-SBA)} \hfill 2021--2026 \\
\textbf{Engineering \& Master’s Degree in Artificial Intelligence} \\
\textit{Master's Thesis: "GPAI-Driven Digital Twin for Industrial Gas Turbines: Bridging System 1/2 for Real-time Prognostics"} \\
Focus: Mamba-SSM, xLSTM, Physics-Informed ML, Edge AI Optimization.

%===========================
\section{TECHNICAL SKILLS}
\textbf{GPAI \& ML}: System 1/2, State-Space Models (Mamba), xLSTM, PINNs, GNN, Reinforcement Learning (DQN), XAI. \\
\textbf{Robotics \& Simulation}: ROS, Webots, Robot Kinematics, Navigation, Manipulation, Synthetic Data Gen. \\
\textbf{Frameworks}: PyTorch, TensorFlow, Keras, Scikit-learn, ONNX, MLflow, Airflow. \\
\textbf{Edge \& Performance}: C++ JIT Compilation, CUDA, Docker, Linux, Real-time Stream Processing (InfluxDB). \\
\textbf{Full-Stack}: FastAPI, Next.js, React, TypeScript, PostgreSQL, Neo4j, WebSockets.

%===========================
\section{RESEARCH \& PROJECT HIGHLIGHTS}

\textbf{Industrial Gas Turbine Digital Twin (Master's Thesis)} \hfill 2025--2026 \\
\textit{Robert Bosch Target: System 1/2, World Models, Edge AI}
\begin{itemize}
    \item Implemented a **System 1/2** architecture for the GE LM2500 turbine: TCNs for rapid perception (System 1) and **Mamba-SSM/xLSTM** for logical trajectory reasoning (System 2).
    \item Developed a **Generative World Model** for "What-If" counterfactual simulations, predicting physical failures with high-fidelity thermodynamic consistency using **PINNs**.
    \item Achieved a record-breaking **0.04ms inference latency** via C++ JIT optimization for edge-based control.
    \item Engineered **XAI heatmaps** using gradient saliency to provide interpretable failure diagnostics.
\end{itemize}

\textbf{GNN-Powered Recruitment Ecosystem (Career Connect)} \hfill 2024--2025 \\
\textit{Robert Bosch Target: Multimodal Perception, Graph-based Reasoning}
\begin{itemize}
    \item Modeled the job market as a graph with **PyTorch Geometric**, using GNNs to infer latent structural relationships.
    \item Integrated **SBERT** and **FAISS** for sub-100ms semantic search across 60,000+ profiles.
\end{itemize}

\textbf{Aura — Advanced AI Trading Ecosystem} \hfill 2025 \\
\textit{Robert Bosch Target: Sequential Decision Making, Reinforcement Learning}
\begin{itemize}
    \item Built a magnitude-aware **DQN Reinforcement Learning** agent for automated market participation.
    \item Developed hybrid LSTM-based temporal models for high-volatility time-series forecasting.
\end{itemize}

\textbf{Mini-GPT \& Vision Transformer (ViT) Implementations} \hfill 2025 \\
\textit{Robert Bosch Target: Generative AI, Transformer Architectures}
\begin{itemize}
    \item Implemented decoder-only and patch-based transformer architectures from scratch in PyTorch.
\end{itemize}

%===========================
\section{LANGUAGES}
English: Fluent (C1) \quad|\quad French: Fluent (C1) \quad|\quad Arabic: Native
\end{document}
