Here is the motivation letter:

\documentclass[11pt]{letter}

\address{Ismail Aissaoui}
{\textit{University of Southampton}, UK, \today}

\signature{}

\begin{document}

\opening{Dear PhD Admissions Committee,}

As a passionate AI and Data Science Engineer, I am thrilled to apply for the PhD position in Artificial Intelligence focusing on biometric recognition systems using machine learning techniques at the University of Southampton. Located in the heart of the UK, this esteemed institution has always been a beacon of innovation and excellence.

My research interests are deeply rooted in machine learning and computer vision, which makes me an ideal candidate for this project. In my previous work, I have developed innovative AI solutions that leverage machine learning techniques to address real-world problems. For instance, my Medical_MambaTS project enabled sub-millisecond bedside inference in cardiovascular medical applications using linear-time state space models. This achievement showcases my ability to design and develop high-performance AI systems that can process complex data streams efficiently.

Furthermore, my PI_DeepONet project demonstrated the power of physics-informed operator networks in predicting cloud forecasting using PyTorch Autograd. This accomplishment highlights my expertise in developing physically constrained AI models that can handle complex datasets. The skills I developed in this project, such as handling missing data and sensor dropouts, are directly applicable to biometric recognition systems.

I am particularly drawn to this PhD opportunity because it allows me to combine my passion for machine learning and computer vision with the cutting-edge artificial intelligence methods and techniques employed in this project. I am confident that my unique blend of skills and experience will enable me to make a significant contribution to the development of novel biometric recognition systems.

Thank you for considering my application. I look forward to discussing my qualifications further.

Sincerely,

Ismail Aissaoui

\closing{\}

\end{document}