\documentclass[a4paper,11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{geometry}
\geometry{left=1.5cm,right=1.5cm,top=1.2cm,bottom=1.2cm}

\usepackage{lmodern}
\usepackage{xcolor}
\definecolor{titleblue}{RGB}{0,51,140}
\definecolor{TITLEBLUE}{RGB}{0,51,140}

\usepackage{hyperref}
\hypersetup{colorlinks=true, urlcolor=titleblue, linkcolor=titleblue}

\usepackage{titlesec}
\usepackage{enumitem}

\pagestyle{empty}

\titleformat{\section}{\color{titleblue}\Large\bfseries\uppercase}{}{0em}{}[\color{titleblue}\titlerule]
\titlespacing\section{0pt}{8pt}{4pt}
\setlist[itemize]{leftmargin=*,topsep=1pt,itemsep=1pt}

\begin{document}

\begin{center}
    {\Huge\bfseries\color{titleblue} AISSAOUI Ismail}\\[4pt]
    {\Large State Engineer in Artificial Intelligence \& Data Science}\\[6pt]
    ismail.aissaoui.pro@gmail.com $|$ +213 660 70 77 96 $|$ Algeria \\
    \href{https://linkedin.com/in/aissaoui-ismail-6a77a92a7}{linkedin.com/in/aissaoui-ismail-6a77a92a7} $|$ \href{https://github.com/i-aissaoui}{github.com/i-aissaoui}
\end{center}

\section{PROFESSIONAL SUMMARY}
State Engineer graduated from ESI-SBA, specializing in Transformers, NLP, Digital Twins, and Industrial AI. Expert in designing end-to-end AI solutions, from metaheuristic optimization to MLOps deployment. PhD candidate focused on transforming industrial systems through hybrid AI and cyber-physical modeling.

\section{WORK EXPERIENCE}
\textbf{AI Engineer Intern — Generative Digital Twin Architecture} \hfill Jan 2026 -- Present \\
\textbf{Sonatrach (Pipeline Transport Branch)} \\
\begin{itemize}
    \item Designed a Generative Surrogate based on \textbf{Mamba-SSM} for real-time "What-If" simulations.
    \item Hardware-Software Co-Design: \textbf{0.04ms} edge inference via \textbf{C++ JIT Compiled xLSTM}.
    \item Integrated \textbf{PINN} (Physics-Informed Neural Networks) to ensure thermodynamic monotonicity.
\end{itemize}

\textbf{Network Engineering Intern} \hfill Sep 2024 \\
\textbf{Algérie Télécom RMC Center}

\section{EDUCATION}
\textbf{National School of Computer Science (ESI-SBA, Algeria)} \hfill 2021 -- 2026 \\
\textbf{State Engineer's Degree \& MSc in Artificial Intelligence}

\section{TECHNICAL SKILLS}
\begin{itemize}
    \item \textbf{AI / Deep Learning}: PyTorch, TensorFlow, Transformers, GNN, GANs, RL (DQN/PPO).
    \item \textbf{Optimization}: PSO, Genetic Algorithms, ACO, Simulated Annealing, Bayesian Optimization.
    \item \textbf{Tech Stack}: Python, FastAPI, Next.js, Docker, MLflow, Kubernetes, CUDA, SQL.
\end{itemize}

\section{RESEARCH \& ENGINEERING PROJECTS}

\textbf{Aura — Adaptive Reinforcement Learning System} \hfill 2025 \\
Institutional-grade trading platform (LSTM + DQN) with real-time WebSocket dashboard.

\textbf{Career Connect — GNN recruitment Intelligence} \hfill 2024 -- 2025 \\
Complex semantic matching using Graph Neural Networks and relational embeddings.

\textbf{Advanced NLP Optimization (Metaheuristics)} \hfill 2025 \\
Multilingual moderation optimized via PSO, GA, and Bayesian optimization (DistilBERT).

\textbf{University Scheduling (NP-Complete Optimization)} \hfill 2025 \\
Automated timetabling via hybrid heuristics (PSO/ACO/GA) for conflict-free allocation.

\textbf{Mini-GPT \& North African Sentiment BERT} \hfill 2025 \\
From-scratch Transformer implementation and LoRA adaptation for Maghrebi dialects.

\textbf{Geo-RAG — Intelligent Map Assistant} \hfill 2025 \\
Geospatial RAG system integrating ChromaDB and GeoPandas for spatial reasoning.

\textbf{Recognizini — Interactive Facial Recognition} \hfill 2025 \\
Online learning system with incremental embeddings and Active Learning feedback loops.

\textbf{Computer Vision \& Industrial Safety (YOLOv8)} \hfill 2025 \\
Traffic analytics (Tracking/OCR) and real-time PPE (Safety Equipment) detection.

\textbf{Synergy POS \& Hadj Logistics} \hfill 2024 -- 2025 \\
Complex logistics and retail solutions (Offline/Online Sync, PostgreSQL/SQLite).

\section{LANGUES}
Arabic (Native), English (Advanced), French (Fluent).

\end{document}
