Here is a highly customized, professional Motivation Letter in LaTeX format:

\documentclass{letter}
\usepackage[margin=0.5in]{geometry}

\address{\centering Ismail Aissaoui}
{\centering AI & Data Science Engineer\\
\centering [Your Address]\\
\centering [City, Country]}

\signature{}

\opening{}

\begin{letter}{PhD Admissions Committee}
\phd{University of Surrey, Surrey, United Kingdom}
\date{\today}

Dear PhD Admissions Committee,

I am excited to apply for the PhD position in AI focusing on tomographic imaging at the University of Surrey. The project's emphasis on robust low-dimensional representations for noisy real-world data resonates deeply with my research interests and expertise.

As a strong candidate, I bring a unique combination of skills and experience. Notably, my work on Medical_MambaTS, a linear-time state space model for sub-millisecond bedside inference, demonstrates my ability to develop innovative solutions that can effectively handle high-dimensional noisy data. In this project, I leveraged the power of machine learning to create a real-time inferencing system, which can be directly applied to tomographic imaging.

I am confident that my expertise in developing robust and efficient algorithms will enable me to make significant contributions to this PhD project. My experience with PyTorch Autograd and 0D Windkessel Physics-Informed Operator Network using PI-DeepONet further solidifies my ability to tackle complex problems in the field of tomographic imaging.

I am particularly drawn to this project because it has the potential to significantly impact the field of tomographic imaging. The collaboration with the National Physical Laboratory and access to resources provided by the Centre for Vision, Speech and Signal Processing CVSSP and the Institute for People-Centred AI at the University of Surrey will enable me to engage in meaningful research that can lead to tangible outcomes.

I am excited about the opportunity to join the University of Surrey's academic community and contribute to the growth of knowledge in this field. I believe my skills, experience, and passion make me an ideal candidate for this PhD position.

Thank you for considering my application. I look forward to discussing my qualifications further.

Sincerely,

Ismail Aissaoui