Here is the motivation letter:

\documentclass[11pt]{letter}

\usepackage{amsmath,amsfonts,amssymb}
\usepackage[margin=1in]{geometry}

\begin{document}

\opening{Dear Admissions Committee,}

I am writing to express my strong interest in pursuing a PhD in Human-Inspired Artificial Intelligence at the University of Cambridge. As a data science engineer with a passion for human-centered AI technologies, I am confident that your esteemed institution will provide me with an ideal environment to grow and contribute to the field.

My background in developing innovative AI solutions, such as Medical_MambaTS, has equipped me with the skills to tackle complex problems. Specifically, my work on linear-time state space models has allowed me to develop sub-millisecond bedside inference capabilities that can be applied to healthcare systems. This achievement demonstrates my ability to create efficient and effective AI solutions that meet real-world needs.

Moreover, I have also worked on robust cloud forecasting using SST_KODA_MultiScale, which leverages 100Hz VitalDB telemetry. This project showcases my capacity for developing scalable and reliable AI models that can handle large datasets. Furthermore, I am well-versed in NLP embeddings using SBERT and PyTorch Geometric, which enables me to create accurate and efficient AI-powered language processing systems.

I am particularly drawn to the University of Cambridge's emphasis on developing human-centered AI technologies. As an advocate for responsible AI development, I believe that it is essential to prioritize the ethical considerations and societal implications of AI deployment. The University's Institute for Technology and Humanity aligns with my values and goals, making me confident that this PhD program will provide a perfect fit.

I am excited about the opportunity to contribute to the university's research community and explore the intersection of human-centered AI technologies. I am confident that my background in AI development, combined with my passion for responsible AI deployment, makes me an ideal candidate for this PhD program.

\closing{Sincerely,}
Ismaïl Aïssouï
\end{document}

Please note that you should replace "Ismaïl Aïssouï" with your actual name.