\documentclass[a4paper,12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{geometry}
\geometry{left=1.8cm,right=1.8cm,top=1.3cm,bottom=1.6cm}

\usepackage{lmodern}
\usepackage{xcolor}

\definecolor{titleblue}{RGB}{0,51,140}
\definecolor{TITLEBLUE}{RGB}{0,51,140}

\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    urlcolor=titleblue,
    linkcolor=titleblue,
    citecolor=titleblue,
    pdfborder={0 0 0}
}

\usepackage{titlesec}
\usepackage{enumitem}

\pagestyle{empty}

\titleformat{\section}
  {\color{titleblue}\Large\bfseries\uppercase}{}{0em}{}
  [\color{titleblue}\titlerule]

\titlespacing\section{0pt}{8pt}{4pt}
\setlist[itemize]{leftmargin=*,topsep=2pt,itemsep=1pt}

\begin{document}

\begin{center}
    {\Huge\bfseries\color{titleblue} AISSAOUI Ismail}\\[4pt]
    {\Large AI \& Data Science Engineer}\\[6pt]

    {\normalsize
    Email: \href{mailto:ismail.aissaoui.pro@gmail.com}{ismail.aissaoui.pro@gmail.com} \quad
    Phone: +213 660 70 77 96 \\
    Portfolio: \href{https://ismail-aissaoui.vercel.app}{ismail-aissaoui.vercel.app} \quad
    Location: Chlef, Algeria \\
    LinkedIn: \href{https://linkedin.com/in/aissaoui-ismail-6a77a92a7}{linkedin.com/in/aissaoui-ismail-6a77a92a7} \quad
    GitHub: \href{https://github.com/i-aissaoui}{github.com/i-aissaoui}
    }
\end{center}

%===========================
\section{PROFILE}
AI \& Data Science Engineer specialized in Human-Computer Interaction (HCI) and intelligent system architecture. Focused on designing new interaction paradigms that treat GenAI as both a \textbf{material and a medium} for mediated action. Expert in building prototypes that explore the redistribution of agency, control, and responsibility between humans and agentic systems.

%===========================
\section{SKILLS}
\setlength{\parskip}{-1pt}
{\normalsize
\textbf{Programming}: Python, TypeScript, JavaScript, Java, SQL \\

\textbf{ML / DL}: PyTorch, TensorFlow, Keras, Scikit-learn, Lightning, \textbf{Agentic Architectures} \\

\textbf{AI \& HCI Techniques}: Interaction Design, \textbf{Mediated Action}, GenAI as Medium, Prototyping \\

\textbf{Optimization}: PSO, Genetic Algorithm, ACO, Simulated Annealing, Bayesian Optimization \\

\textbf{Web \& API}: React, Next.js, FastAPI, Node.js, TailwindCSS \\

\textbf{Data \& MLOps}: MLflow, Airflow, Kubeflow, DVC, Pandas, NumPy \\

\textbf{Databases}: PostgreSQL, MongoDB, MySQL, Neo4j, Cassandra \\

\textbf{Cloud \& DevOps}: Docker, Linux, Git, CI/CD, CUDA, AWS, Grafana \\

\textbf{Research \& HCI}: User Studies, Qualitative/Quantitative Methods, Statistics, Human-Centered Design, Mediated Action \\

\textbf{Soft Skills}: Technical leadership, Scientific communication, Interdisciplinary collaboration
}

%===========================
\section{PROFESSIONAL EXPERIENCE}
\textbf{AI Engineer Intern — Digital Twin \& Predictive Maintenance} \hfill 2026 \\
Sonatrach — Algeria \\
Developed a Digital Twin for gas turbines enabling real-time monitoring and predictive maintenance. Implemented advanced anomaly detection and RUL estimation using deep learning models.

\textbf{Network Engineering Intern} \hfill Sep 2024 \\
Algérie Télécom RMC Center — Chlef, Algeria

%===========================
\section{EDUCATION}
\textbf{National Higher School of Computer Science (ESI-SBA)} \hfill 2021--2026 \\
Engineering and Master’s Degree in Computer Science \\
Specialization: Artificial Intelligence \& Informatics

%===========================
\section{KEY ACHIEVEMENTS}
\begin{itemize}
    \item Developed custom Transformer models (BERT, GPT, RAG) for real-world multilingual applications.
    \item Built explainable AI platforms for HR tech and public institutions — reducing bias and improving decision quality.
    \item Designed a graph-based recommendation system with +24\% accuracy improvement (dataset: 60K profiles).
    \item Delivered complete ML pipelines: data ingestion, validation, training, CI/CD, and monitoring.
    \item Built real-time vision systems (YOLO, ByteTrack) reducing latency by 32\%.
\end{itemize}

%===========================
% Force projects + languages onto page 2
\newpage

\section{PROJECTS}
% tighter spacing so everything fits on page 2
\setlength{\parskip}{10pt}
{\small

\textbf{Spatial Interaction \& Geo-RAG} \hfill 2025 \\
Architected a map-oriented assistant where GenAI acts as a mediating substrate. Addressed the \textbf{gulf of execution} by simplifying intent expression and implementing dynamic context maintenance using latent embeddings. \\
\textit{Tech: ChromaDB, LangChain, React — Concepts: Mediated Action, Context Maintenance, Medium}

\textbf{Aura — Enterprise AI Trading System} \hfill 2025 \\
Full-stack automated crypto trading platform powered by hybrid LSTM forecasting and \textbf{Reinforcement Learning} (Deep Q-Learning) to optimize entry/exit policies under long-term reward maximization. Includes advanced technical indicators, real-time dashboards, and interactive backtesting. \\
\textit{Tech: TensorFlow, Keras, FastAPI, Next.js, WebSockets — Concepts: LSTM, Reinforcement Learning, Deep Q-Learning, Time-Series Analysis}

\textbf{Advanced NLP Pipeline with Multi-Optimization} \hfill 2025 \\
Multilingual moderation optimized with PSO, Genetic Algorithm, and Bayesian Optimization. \\
\textit{Tech: DistilBERT, PyTorch, FastAPI — Concepts: Optimization, Transformers, Classification}

\textbf{Intelligent University Scheduler} \hfill 2025 \\
Automatic generation of conflict-free timetables using hybrid heuristics and evolutionary algorithms. \\
\textit{Tech: FastAPI, NumPy, Pandas — Concepts: GA, PSO, ACO, Simulated Annealing}

\textbf{Mini-GPT (Decoder-only)} \hfill 2025 \\
Implementation of a compact GPT model with controlled training and sequential text generation. \\
\textit{Tech: PyTorch, CUDA, AdamW, W\&B — Concepts: Transformers, Language Modeling}

\textbf{North African Sentiment BERT} \hfill 2025 \\
LoRA adaptation of BERT for sentiment analysis in Maghrebi dialect. \\
\textit{Tech: PyTorch, LoRA, MLflow — Concepts: Fine-tuning, Low-Rank Adaptation}

\textbf{Geo-RAG — Map Assistant} \hfill 2025 \\
RAG system integrating geospatial data for map-oriented queries. \\
\textit{Tech: ChromaDB, GeoPandas, Streamlit — Concepts: RAG, Spatial Reasoning}

\textbf{Recognizini — Agency Redistribution} \hfill 2025 \\
Hybrid facial recognition system exploring responsibility redistribution through an \textbf{iterative feedback loop}. Users act "through" the system to correct and guide inference in real-time. \\
\textit{Tech: OpenCV, PyTorch, React — Concepts: Agency, Human-Centric AI, Control Architectures}

\textbf{Real-time PPE Detection (YOLOv8)} \hfill 2025 \\
Real-time detection of safety equipment (helmet, vest) for compliance monitoring. \\
\textit{Tech: YOLOv8, OpenCV — Concepts: Object Detection, Streaming}

\textbf{Traffic Analytics Suite} \hfill 2025 \\
Traffic analytics including tracking, speed estimation, and license plate recognition. \\
\textit{Tech: YOLOv8, ByteTrack, EasyOCR — Concepts: Tracking, OCR, Analytics}

\textbf{Hadj Management System} \hfill 2024 \\
End-to-end logistics platform for group management and itineraries. \\
\textit{Tech: React, FastAPI, PostgreSQL — Concepts: Workflow, Synchronization}

\textbf{Hybrid POS \& E-Commerce System} \hfill 2025 \\
Offline-first POS system integrated with an online store. \\
\textit{Tech: PyQt, SQLite, PostgreSQL — Concepts: Offline/Online Sync, Inventory Management}

} % end small

%===========================
\section{LANGUAGES}
Arabic: Mother Tongue \quad|\quad English: Advanced \quad|\quad French: Conversational

\end{document}
