\documentclass[11pt]{letter}

\address{\begin{tabular}{@{}l@{}}123 Main Street\\Anytown, USA 12345\end{tabular}}

\signature{\begin{tabular}{@{}l@{}}Ismail Aissaoui\end{tabular}}

\date{\today}

\opening{\noindent To the Admissions Committee at University of Southampton}

Dear Sir/Madam,

I am writing to express my strong interest in pursuing a PhD degree in AI-driven silicon photonics circuits design at the University of Southampton, located in Southampton, United Kingdom. As a highly motivated and skilled AI & Data Science Engineer, I believe that this PhD program would be an ideal fit for me.

With a solid foundation in computer science and electronics engineering, my most recent project, "Cardiovascular Medical Digital Twin," has showcased my ability to develop innovative solutions that combine AI with real-world engineering challenges. Specifically, I would like to highlight the following achievements that demonstrate my expertise in areas relevant to this PhD offer:

\begin{itemize}
\item Medical_MambaTS: My linear-time state space model for sub-millisecond bedside inference showcases my ability to design efficient algorithms that can be applied to the development of AI-driven photonic circuits. This achievement demonstrates my capacity to create fast and accurate models, a crucial aspect in the inverse design approach.
\item PI_DeepONet: As a Physics-Informed Operator Network using PyTorch Autograd, this achievement highlights my understanding of physical constraints and their application in AI-driven systems. This skill is essential in designing photonic circuits that can efficiently interact with their environment.
\end{itemize}

I am particularly drawn to this PhD program because it offers the opportunity to bring my skills in machine learning and optimisation into the rapidly evolving field of photonics. The project's focus on applying AI to inverse design, a method that works backwards from desired performance to generate efficient photonic circuits, aligns with my research interests and goals.

I am confident that my academic background, research experience, and passion for innovation make me an ideal candidate for this PhD program. I would be thrilled to bring my expertise to the University of Southampton and contribute to the development of AI-driven silicon photonics circuits design.

Thank you for considering my application. I look forward to the opportunity to discuss my qualifications further.

Sincerely,

Ismail Aissaoui