Here is the motivation letter in LaTeX format:

\documentclass{letter}

\begin{document}

\opening{Dear Admissions Committee,}

I am writing to express my enthusiastic interest in pursuing a PhD at the University of Southampton under the project "Shadow Tomography for In-Context Quantum Machine Learning". I am impressed by the university's cutting-edge research in artificial intelligence and its applications in quantum computing.

As an AI & Data Science Engineer with a strong computational background, I believe my skills align perfectly with the requirements of this PhD offer. My most relevant achievement that resonates with this project is my development of Medical_MambaTS - a linear-time state space model for sub-millisecond bedside inference. This achievement demonstrates my ability to design efficient algorithms for high-speed decision-making, which is crucial in quantum computing where encoding and extracting information from a quantum state that undergoes unitary evolution has been the principal bottleneck.

Moreover, my work on PI_DeepONet - a 0D Windkessel Physics-Informed Operator Network using PyTorch Autograd - showcases my proficiency in handling physical constraints and complex systems. In this context, I believe I can bring valuable insights to designing transformer-inspired quantum circuit architectures that incorporate physical constraints from the observation of "in-context learning" in large language models.

I am particularly drawn to this project because it leverages ideas from observation of "in-context learning" in large language models into quantum computing, which aligns with my passion for exploring the intersection of AI and physics. I am confident that my skills and experience will enable me to make a meaningful contribution to this project and produce high-quality research.

Thank you for considering my application. I look forward to discussing my qualifications further.

Sincerely,

Ismail Aissaoui

\closing{}

\end{document}