\documentclass[a4paper,11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{geometry}
\geometry{left=1.5cm,right=1.5cm,top=1.2cm,bottom=1.2cm}

\usepackage{lmodern}
\usepackage{xcolor}
\definecolor{titleblue}{RGB}{0,51,140}
\definecolor{TITLEBLUE}{RGB}{0,51,140}

\usepackage{hyperref}
\hypersetup{colorlinks=true, urlcolor=titleblue, linkcolor=titleblue}

\usepackage{titlesec}
\usepackage{enumitem}

\pagestyle{empty}

\titleformat{\section}{\color{titleblue}\Large\bfseries\uppercase}{}{0em}{}[\color{titleblue}\titlerule]
\titlespacing\section{0pt}{8pt}{4pt}
\setlist[itemize]{leftmargin=*,topsep=1pt,itemsep=1pt}

\begin{document}

\begin{center}
    {\Huge\bfseries\color{titleblue} AISSAOUI Ismail}\\[4pt]
    {\Large State Engineer in Artificial Intelligence \& Data Science}\\[6pt]
    ismail.aissaoui.pro@gmail.com $|$ +213 660 70 77 96 $|$ Algeria \\
    \href{https://linkedin.com/in/aissaoui-ismail-6a77a92a7}{linkedin.com/in/aissaoui-ismail-6a77a92a7} $|$ \href{https://github.com/i-aissaoui}{github.com/i-aissaoui}
\end{center}

\section{PROFESSIONAL SUMMARY}
State Engineer graduated from ESI-SBA, specializing in \textbf{Graph Neural Networks (GNN)}, Federated Learning, and the cybersecurity of Cyber-Physical Systems (CPS). Expert in structural modeling and centrality measures for distributed intrusion detection.

\section{EDUCATION}
\textbf{National School of Computer Science (ESI-SBA, Algeria)} \hfill 2021 -- 2026 \\
\textbf{State Engineer's Degree \& MSc in Artificial Intelligence}

\section{RESEARCH & ENGINEERING PROJECTS}

\textbf{Career Connect — GNN recruitment Intelligence} \hfill 2024 -- 2025 \\
Architected a \textbf{Graph Neural Networks} system for complex semantic matching.
\begin{itemize}
    \item Modeled heterogeneous relationships using graph embeddings.
    \item Utilized centrality measures to identify pivotal nodes in dense networks.
    \textit{Direct Match: Expertise in GNN and complex network theory.}
\end{itemize}

\textbf{Generative Digital Twin — Sonatrach} \hfill 2026 \\
Distributed inference and anomaly detection for complex industrial systems.
\begin{itemize}
    \item Implemented \textbf{Mamba-SSM} and \textbf{xLSTM} for real-time monitoring.
    \item Secured Edge-Cloud data flow using Physics-Informed Neural Networks (PINN).
\end{itemize}

\textbf{University Scheduling (NP-Complete Optimization)} \hfill 2025 \\
Automated resource allocation using hybrid metaheuristics (\textbf{PSO/ACO/GA}).

\textbf{Aura — Adaptive Reinforcement Learning System} \hfill 2025 \\
Trading platform with distributed real-time data pipelines and DQN agents.

\textbf{Geo-RAG — Geospatial Knowledge Retrieval} \hfill 2025 \\
Semantic reasoning and RAG system for multi-source geospatial data.

\section{WORK EXPERIENCE}
\textbf{AI Engineer Intern} \hfill Jan 2026 -- Present \\
\textbf{Sonatrach (Pipeline Transport Branch)} \\
Predictive maintenance and software architecture for Digital Twins.

\textbf{Network Engineering Intern} \hfill Sep 2024 \\
\textbf{Algérie Télécom RMC Center}

\section{TECHNICAL SKILLS}
\begin{itemize}
    \item \textbf{Graph AI}: GNN (GraphSAGE, GAT), Centrality, PyTorch Geometric, NetworkX.
    \item \textbf{Distributed AI}: Federated Learning (architecture), Privacy-preserving AI.
    \item \textbf{Deep Learning}: PyTorch, Mamba-SSM, Transformers, PINN, RL.
    \item \textbf{Security \& Dev}: Intrusion Detection Systems (IDS), C++, Python, Docker, MLflow.
\end{itemize}

\section{LANGUES}
Arabic (Native), English (Advanced), French (Fluent).

\end{document}
