\documentclass{letter}

\begin{document}

\address{\noindent
Max Planck Gesellschaft\\
Munich, Germany}

\signature{\noindent
Ismail Aissaoui}

\opening{\noindent June 15, 2026}

Dear Sachse and Georgopoulou,

I am writing to express my strong interest in the PhD position on embodied intelligence through material, mechanics, and computation at the Max Planck Gesellschaft. With a Master's degree in mechanical engineering and a passion for robotics, I believe my skills and research experience make me an ideal candidate for this opportunity.

In my previous work, I developed Medical_MambaTS, a linear-time state space model capable of providing sub-millisecond bedside inference. This achievement resonates with the focus on adaptive materials and computational design methods required in this PhD position. The low latency and robustness of MambaTS can be leveraged to develop novel embodied intelligence systems that seamlessly integrate physical and computational components.

I am particularly drawn to this project because it combines my interests in robotics, materials science, and computation. As an AI & Data Science Engineer, I have a strong foundation in machine learning and programming languages such as PyTorch and Python. I am confident that my skills will enable me to contribute significantly to the development of adaptive materials and computational design methods for embodied intelligence.

I look forward to discussing my application with you further. Please do not hesitate to contact me if you require any additional information.

Sincerely,

\closing{\noindent
Ismail Aissaoui}

\end{document}