\documentclass[11pt, a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\usepackage{titlesec}

\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]

\begin{document}
\begin{center}
    {\LARGE \textbf{Applicant Profile \& Supplementary Information}} \\
    \vspace{0.2cm}
    Ismail Aissaoui \\
    \href{https://ismail-aissaoui.vercel.app}{https://ismail-aissaoui.vercel.app}
\end{center}

\section*{Links to Code and Theses}
\begin{itemize}
    \item \textbf{GitHub Repository:} \href{https://github.com/IsmailAissaoui}{https://github.com/IsmailAissaoui}
    \item \textbf{Master's Thesis (Cardiovascular Medical Digital Twin):} \href{https://ismail-aissaoui.vercel.app}{Available via Academic Portfolio}
    \item \textbf{State Engineer Thesis (Gas Turbine Digital Twin):} \href{https://ismail-aissaoui.vercel.app}{Available via Academic Portfolio}
\end{itemize}

\section*{Record of Academic Courses \& Grading}
\textit{Institution: Ecole Supérieure en Informatique de Sidi Bel-Abbès (ESI-SBA)} \\
\textit{System: 0-20 scale (10 is passing; \textgreater 14 is Very Good; \textgreater 16 is Excellent)}
\begin{itemize}
    \item \textbf{Core Mathematics \& Theory:} Calculus, Linear Algebra, Probability \& Statistics, Optimization Theory.
    \item \textbf{Computer Science \& AI:} Machine Learning, Deep Learning, Computer Vision, Signal Processing, Data Structures \& Algorithms.
    \item \textit{Note: Full official academic transcripts and translated degree certificates are available upon request or upon formal enrollment.}
\end{itemize}

\section*{Key Academic Projects}
\textbf{1. Cardiovascular Medical Digital Twin (Master's Thesis)} \\
\textit{Contribution:} Engineered "Medical\_MambaTS", a linear-time state-space model for sub-millisecond bedside inference. Developed PI-DeepONet, a Physics-Informed Operator Network that explicitly maps 0D Windkessel differential equations into the neural architecture via PyTorch Autograd. Designed a "Missingness-Aware Gate" to dynamically handle sensor dropouts in ICU data.

\vspace{0.2cm}

\textbf{2. Gas Turbine Digital Twin (State Engineer Thesis)} \\
\textit{Contribution:} Built predictive maintenance architectures using ST-KDFormer and Temporal Convolutional Networks to predict thermodynamic degradation and sensor drift in complex rotating machinery. Validated against real-world, high-frequency SCADA telemetry.

\end{document}
