\documentclass[11pt, a4paper]{letter}
\usepackage[utf8]{inputenc}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}

\begin{document}
\begin{letter}{Dr. Kevin Groot Lipman \\ fomo.fo lab \\ Netherlands Cancer Institute}
\opening{Dear Dr. Kevin Groot Lipman and the Hiring Committee,}

I am writing to express my strong interest in the PhD Student position focusing on Foundation Models for Oncology at the Netherlands Cancer Institute (NKI) and the University of Amsterdam.

As an AI \& Data Science Engineer specializing in medical deep learning, I am highly motivated by the challenge of applying large-scale foundation models to clinical oncology. During my "Cardiovascular Medical Digital Twin" Master's thesis, I built architectures capable of handling complex, real-world clinical data. Specifically, I engineered a "Missingness-Aware Gate" to dynamically handle sensor dropouts and sparse clinical records without corrupting the latent state of the model. I also engineered Medical\_MambaTS, a linear-time state-space model that ensures mathematical stability during long-context medical inference. 

I believe my experience in robust, high-frequency medical modeling and handling missing clinical data perfectly aligns with the complexities of multi-modal oncology foundation models. The clinical focus of the fomo.fo lab—specifically the goal of moving beyond narrow task-specific models to general-purpose patient representations—is the exact research trajectory I wish to pursue for my doctorate.

Please find attached my complete application package, including my research statement and technical portfolio. 

Thank you for your time and consideration. I would welcome the opportunity to discuss my qualifications with you in an interview.

\closing{Sincerely, \\ Ismail Aissaoui \\ \href{https://ismail-aissaoui.vercel.app}{https://ismail-aissaoui.vercel.app}}
\end{letter}
\end{document}