Here is the motivation letter:

\documentclass{letter}

\address{\thefamily}
{\begin{tabular}{@{}c@{}} Ismail Aissaoui \\ [5mm] \end{tabular}}

\opening{\begin{tabular}{@{}l@{}} Delft, Netherlands \\ \end{tabular}\vspace{-2.5mm}June 15, 2026\hspace{-2.5mm}\\[1mm]\vspace{1mm}}
To the PhD Admissions Committee at Delft University of Technology,

\begin{letter}

Dear Admissions Committee,

I am excited to apply for the fully funded PhD position on "The Impact of AI on Business Operations in Knowledge-Intensive Technology Firms" at the Delft University of Technology. As a passionate AI and Data Science Engineer, I am drawn to this opportunity to investigate how AI transforms core business functions within knowledge-intensive firms.

With my background in relevant fields and strong quantitative research skills, I believe I can make a meaningful contribution to this project. Specifically, my achievements in the "Cardiovascular Medical Digital Twin" project have prepared me well for this PhD offer. For instance, my work on PI_DeepONet, a Physics-Informed Operator Network using PyTorch Autograd, demonstrates my ability to integrate AI into complex systems with physical constraints, which aligns perfectly with the research focus on AI's impact on business operations.

Moreover, my experience with SST_KODA_MultiScale, a robust cloud forecasting system that handles missing data, showcases my capability to develop AI-powered solutions for real-world problems. I am confident that my skills in NLP embeddings using SBERT and PyTorch Geometric will also be valuable assets in this project.

I am impressed by the university's reputation for cutting-edge research and its focus on interdisciplinary collaboration. I am excited about the prospect of joining a fully funded PhD program at Delft University of Technology and contributing to the shaping of our understanding of AI's impact on business operations.

Thank you for considering my application. I look forward to discussing this opportunity further.

Sincerely,

Ismail Aissaoui

\end{letter}

\closing{\end{letter}}
\end{document}