\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{titlesec}

\geometry{margin=1in}
\definecolor{titleblue}{RGB}{0,51,102}

\hypersetup{
    colorlinks=true,
    linkcolor=titleblue,
    urlcolor=titleblue,
    pdftitle={Cover Letter - Ismail AISSAOUI},
}

\begin{document}

\noindent \textbf{Ismail AISSAOUI} \\
State Engineer in Artificial Intelligence (ESI-SBA) \\
Email: ismail.aissaoui@example.com \\
Phone: [Your Phone Number] \\
LinkedIn: [Your Link]

\bigskip

\begin{flushright}
    To the Recruitment Committee \\
    \textbf{University of Geneva (UNIGE)} \\
    GSEM - Research Institute for Statistics (RISIS) \\
    Attn: Professor Sebastian Engelke \\
    \medskip
    May 4, 2026
\end{flushright}

\bigskip

\noindent \textbf{Subject: Application for PhD Candidate / Research and Teaching Assistant position (Ref: 6889)}

\bigskip

Dear Professor Engelke,

I am writing to formally submit my application for the PhD Candidate and Teaching Assistant position at the RISIS Institute, University of Geneva. As a State Engineer in Artificial Intelligence from ESI-SBA, I am eager to join your research group to conduct statistical analysis of AI weather forecasting models at the intersection of Extreme Value Theory and Climate Sciences.

My application is supported by a personal recommendation from **Prof. Vincent Cheutet (INSA Lyon)**, who identified my background in Graph Neural Networks (GNNs) and hybrid modeling as a strong match for your group's focus on complex AI architectures like **GraphCast** and **AIFS**.

Currently, for my thesis at Sonatrach, I am developing **Physics-Informed Digital Twins** for the monitoring of industrial systems. This work has allowed me to master the mathematical and practical aspects of several domains directly relevant to your research:
\begin{itemize}
    \item \textbf{Graph-based AI}: I have extensive experience with GNNs, which are the backbone of GraphCast. I am particularly interested in how the message-passing mechanisms on multi-mesh grids can be statistically analyzed to understand their behavior during extreme events.
    \item \textbf{Sequential Dynamics}: I utilize State Space Models (\textbf{Mamba-SSM}) and \textbf{xLSTM} for trajectory forecasting. My experience with these architectures provides a solid foundation for analyzing the long-range temporal dependencies in climate models.
    \item \textbf{Model Reliability}: My research on "Validity Envelopes" for Digital Twins shares a core objective with your focus on robustness and extremes: ensuring that AI models remain reliable when extrapolating to rare or unseen scenarios.
\end{itemize}

Beyond research, I am highly motivated by the **Teaching Assistant** aspect of this position. I possess the self-discipline and communication skills required to lead tutorials and supervise Master’s students, and I look forward to contributing to the academic life of the GSEM.

I am confident that my technical proficiency in Python and my engineering-grounded perspective on AI will bring a valuable "model-centric" approach to your statistical analysis of climate extremes.

Thank you for considering my application. I look forward to the possibility of discussing my research interests with you.

Sincerely,

\bigskip

\noindent Ismail AISSAOUI

\end{document}
