\documentclass[a4paper,11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{geometry}
\geometry{left=1.5cm,right=1.5cm,top=1.2cm,bottom=1.2cm}

\usepackage{lmodern}
\usepackage{xcolor}
\definecolor{titleblue}{RGB}{0,51,140}
\definecolor{TITLEBLUE}{RGB}{0,51,140}

\usepackage{hyperref}
\hypersetup{colorlinks=true, urlcolor=titleblue, linkcolor=titleblue}

\usepackage{titlesec}
\usepackage{enumitem}

\pagestyle{empty}

\titleformat{\section}{\color{titleblue}\Large\bfseries\uppercase}{}{0em}{}[\color{titleblue}\titlerule]
\titlespacing\section{0pt}{8pt}{4pt}
\setlist[itemize]{leftmargin=*,topsep=1pt,itemsep=1pt}

\begin{document}

\begin{center}
    {\Huge\bfseries\color{titleblue} AISSAOUI Ismail}\\[4pt]
    {\Large State Engineer in Artificial Intelligence \& Data Science}\\[6pt]
    ismail.aissaoui.pro@gmail.com $|$ +213 660 70 77 96 $|$ Algeria \\
    \href{https://linkedin.com/in/aissaoui-ismail-6a77a92a7}{linkedin.com/in/aissaoui-ismail-6a77a92a7} $|$ \href{https://github.com/i-aissaoui}{github.com/i-aissaoui}
\end{center}

\section{RESEARCH SUMMARY}
State Engineer (ESI-SBA) with a focus on \textbf{Structural Generalization} and \textbf{Sequence Modeling}. Expert in transformer alternatives (\textbf{Mamba-SSM}), Graph Neural Networks, and algorithmic optimization. Strong background in mathematical foundations of Deep Learning.

\section{EDUCATION}
\textbf{National School of Computer Science (ESI-SBA, Algeria)} \hfill 2021 -- 2026 \\
\textbf{State Engineer's Degree \& MSc in Artificial Intelligence}

\section{RESEARCH PROJECTS}

\textbf{Generative Surrogate Architectures (Mamba-SSM)} \hfill 2026 \\
Research on structural generalization for sequence-to-sequence modeling in industrial CPS.
\begin{itemize}
    \item Developed a generative simulator using \textbf{Mamba-SSM} to handle long-range dependencies.
    \item Implemented \textbf{xLSTM} with C++ JIT for high-speed structural inference.
    \item Investigated \textbf{Koopman Theory} for linearizing non-linear structural dynamics.
\end{itemize}

\textbf{Career Connect — Structural GNN Intelligence} \hfill 2024 -- 2025 \\
Architected \textbf{Graph Neural Networks} for semantic structural matching.
\begin{itemize}
    \item Researched heterogeneous relation embeddings and network centrality.
    \item Focused on generalization across diverse relational structures.
\end{itemize}

\textbf{NLP Optimization — DistilBERT \& Metaheuristics} \hfill 2025 \\
Hyperparameter optimization for transformer-based LLMs using PSO and GA.

\textbf{Geo-RAG — Semantic Knowledge Retrieval} \hfill 2025 \\
RAG system for multi-source knowledge extraction and structural reasoning.

\section{TECHNICAL SKILLS}
\begin{itemize}
    \item \textbf{Sequence Modeling}: Transformers, Mamba-SSM, xLSTM, Informer, TCN.
    \item \textbf{Graph AI}: GNN (GraphSAGE, GAT), Structural Centrality, PyG.
    \item \textbf{Mathematics}: Linear Algebra, Optimization (PSO, GA), PINN, Koopman Theory.
    \item \textbf{Engineering}: PyTorch, C++, Docker, MLflow, CUDA, Linux.
\end{itemize}

\section{LANGUAGES}
Arabic (Native), English (Advanced - Professional Research Level), French (Fluent).

\end{document}
