\documentclass{letter}

\begin{document}

\opening{Dear PhD Admissions Committee,}

I am excited to apply for the PhD position "Designing smart space structures for extreme environments: from nonlinear dynamics to resilient mechanisms" at the University of Southampton, located in Southampton, United Kingdom. As a highly motivated and skilled AI & Data Science Engineer, I believe my research experience and achievements make me an ideal candidate for this project.

In my previous work on the "Cardiovascular Medical Digital Twin" project, I developed several innovative methods that can be directly applied to the requirements of this PhD offer. Specifically, I would like to highlight two achievements that demonstrate my expertise in nonlinear dynamics and resilient mechanisms: Medical_MambaTS and PI_DeepONet.

Medical_MambaTS is a linear-time state space model for sub-millisecond bedside inference. This achievement showcases my ability to develop mathematical models that can handle high-dimensional data and achieve real-time processing, which is crucial for the development of AI-based predictive control methods for resilient space structures. Moreover, Medical_MambaTS' linear-time complexity ensures efficient computation, a critical aspect in the design of smart space structures.

PI_DeepONet, on the other hand, is a 0D Windkessel Physics-Informed Operator Network using PyTorch Autograd. This achievement demonstrates my understanding of physical constraints and their incorporation into machine learning models. In the context of this PhD project, PI_DeepONet's ability to handle physical constraints can be applied to the development of resilient mechanisms for space structures.

In addition to these achievements, I possess a strong background in dynamics and control, with skills in numerical modeling and machine learning. I am confident that my unique combination of research experience and technical expertise makes me an ideal candidate for this PhD position.

I am excited about the opportunity to work on this project and contribute to the development of smart space structures for extreme environments. I am confident that my skills and achievements make me a strong candidate, and I look forward to discussing my application with you further.

\closing{Sincerely,}

Ismail Aissaoui

\end{document}