\documentclass[a4paper,12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{geometry}
\geometry{left=1.8cm,right=1.8cm,top=1.3cm,bottom=1.6cm}

\usepackage{lmodern}
\usepackage{xcolor}

\definecolor{titleblue}{RGB}{0,51,140}
\definecolor{TITLEBLUE}{RGB}{0,51,140}

\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    urlcolor=titleblue,
    linkcolor=titleblue,
    citecolor=titleblue,
    pdfborder={0 0 0}
}

\usepackage{titlesec}
\usepackage{enumitem}

\pagestyle{empty}

\titleformat{\section}
  {\color{titleblue}\Large\bfseries\uppercase}{}{0em}{}
  [\color{titleblue}\titlerule]

\titlespacing\section{0pt}{8pt}{4pt}
\setlist[itemize]{leftmargin=*,topsep=2pt,itemsep=1pt}

\begin{document}

\begin{center}
    {\Huge\bfseries\color{titleblue} AISSAOUI Ismail}\\[4pt]
    {\Large AI \& Data Science Engineer}\\[6pt]

    {\normalsize
    Email: \href{mailto:ismail.aissaoui.pro@gmail.com}{ismail.aissaoui.pro@gmail.com} \quad
    Phone: +213 660 70 77 96 \\
    Portfolio: \href{https://ismail-aissaoui.vercel.app}{ismail-aissaoui.vercel.app} \quad
    Location: Chlef, Algeria \\
    LinkedIn: \href{https://linkedin.com/in/aissaoui-ismail-6a77a92a7}{linkedin.com/in/aissaoui-ismail-6a77a92a7} \quad
    GitHub: \href{https://github.com/i-aissaoui}{github.com/i-aissaoui}
    }
\end{center}

%===========================
\section{PROFILE}
AI \& Data Science Engineer passionate about human-computer interaction and adaptive learning systems. Expertise in Transformer models, Reinforcement Learning, and Digital Twins. PhD candidate for co-learning in XR, aiming to merge embodied AI and technical gesture simulation for advanced training environments.

%===========================
\section{SKILLS}
\setlength{\parskip}{-1pt}
{\normalsize
\textbf{Programming}: Python, TypeScript, JavaScript, Java, SQL \\

\textbf{AI / ML}: PyTorch, TensorFlow, Keras, Scikit-learn, \textbf{Inverse RL}, \textbf{Imitation Learning} \\

\textbf{AI Techniques}: Transformers, GNN, GANs, RL (DQN, PPO), \textbf{Symbolic AI} (Rule-based systems) \\

\textbf{Optimization}: PSO, Genetic Algorithm, ACO, Simulated Annealing, Bayesian Optimization \\

\textbf{Web, API \& 3D}: Next.js, FastAPI, Node.js, \textbf{Unity3D}, \textbf{Unreal Engine (C++)} \\

\textbf{Data \& MLOps}: MLflow, Airflow, Kubeflow, DVC, Pandas, NumPy \\

\textbf{Databases}: PostgreSQL, MongoDB, MySQL, Neo4j, Cassandra \\

\textbf{Cloud \& DevOps}: Docker, Linux, Git, CI/CD, CUDA, AWS, Grafana \\

\textbf{Soft Skills}: Technical leadership, Communication, Stakeholder management
}

%===========================
\section{PROFESSIONAL EXPERIENCE}
\textbf{AI Engineer Intern — Digital Twin \& Simulation} \hfill 2026 \\
Sonatrach — Algeria \\
Developed a Digital Twin for real-time supervision of gas turbines. Modeled physical flows and estimated RUL using Deep Learning. This immersion in high-fidelity simulation enabled me to master the digital replication of complex industrial processes, a cornerstone for immersive training systems.

\textbf{Network Engineering Intern} \hfill Sep 2024 \\
Algérie Télécom RMC Center — Chlef, Algeria

%===========================
\section{EDUCATION}
\textbf{National Higher School of Computer Science (ESI-SBA)} \hfill 2021--2026 \\
Engineering and Master’s Degree in Computer Science \\
Specialization: Artificial Intelligence \& Informatics

%===========================
\section{KEY ACHIEVEMENTS}
\begin{itemize}
    \item Developed custom Transformer models (BERT, GPT, RAG) for real-world multilingual applications.
    \item Built explainable AI platforms for HR tech and public institutions — reducing bias and improving decision quality.
    \item Designed a graph-based recommendation system with +24\% accuracy improvement (dataset: 60K profiles).
    \item Delivered complete ML pipelines: data ingestion, validation, training, CI/CD, and monitoring.
    \item Built real-time vision systems (YOLO, ByteTrack) reducing latency by 32\%.
\end{itemize}

%===========================
% Force projects + languages onto page 2
%===========================
\section{PROJECTS}
\setlength{\parskip}{6pt}
{\small

\textbf{Aura — Adaptive Reinforcement Learning System} \hfill 2025 \\
Developed an autonomous agent using \textbf{Reinforcement Learning} (DQN) for real-time strategy optimization. Implemented adaptive policies allowing the system to continuously learn from its environment. \\
\textit{Tech: TensorFlow, RL, Python — Concepts: Reinforcement Learning, Adaptability}

\textbf{Vision Transformer (ViT) Implementation} \hfill 2025 \\
Adapted Transformer architectures for Computer Vision. Treated images as sequences of patches, using multi-head self-attention to capture global dependencies. \\
\textit{Tech: PyTorch, Deep Learning — Concepts: Transformers, Image-to-Sequence}

\textbf{Recognizini — Online Learning \& Interactive Feedback} \hfill 2025 \\
Real-time facial recognition system integrating human feedback loop for incremental identity learning. Used \textbf{Label Propagation} to dynamically enrich the model. \\
\textit{Tech: PyTorch, OpenCV, FastAPI — Concepts: Ecological Learning, Feedback Loop}

\textbf{Traffic Analytics \& Safety Monitoring (YOLOv8)} \hfill 2025 \\
Analyzed video data streams for object tracking and trajectory estimation. Provides a solid foundation for modeling and evaluating \textbf{technical gestures} in real-time. \\
\textit{Tech: YOLOv8, Computer Vision — Concepts: Motion Analysis, Action Tracking}

\textbf{GNN-based Recruitment Intelligence} \hfill 2024--2025 \\
Modeled complex relationships between skills and profiles using \textbf{Graph Neural Networks}. Expertise in extracting rich semantic representations from knowledge graphs. \\
\textit{Tech: PyTorch Geometric, SBERT — Concepts: Graph Learning, Knowledge Modeling}

\textbf{Mini-GPT \& Deep NLP Adaptation} \hfill 2025 \\
Implemented GPT (Decoder-only) architectures and LoRA adaptation for BERT models on multilingual and dialectal sentiment analysis tasks. \\
\textit{Tech: PyTorch, LoRA, HuggingFace — Concepts: LLM, Fine-tuning, NLP}

\textbf{Geo-RAG \& Intelligent Scheduling} \hfill 2025 \\
Developed geospatial RAG systems and metaheuristic algorithms (GA, PSO) for solving complex NP-complete constraint optimization problems. \\
\textit{Tech: ChromaDB, LangChain, NumPy — Concepts: RAG, Optimization}

\textbf{Elliptic++ : Bitcoin Fraud Detection} \hfill 2025 \\
Detected illicit actors on the Bitcoin network via graph-based learning on over 200k transactions. \\
\textit{Tech: PyTorch Geometric, NetworkX — Concepts: Fraud Detection, GNN}
}

%===========================
\section{LANGUAGES}
Arabic: Mother Tongue \quad|\quad English: Advanced \quad|\quad French: Conversational

\end{document}
