Here is the motivation letter:

\documentclass{letter}

\begin{document}

\address{\noindent University of Southampton \\ Integrated Polysilicon Photonics \\ Southampton, United Kingdom}

\opening{\noindent To Whom It May Concern}

As a passionate AI and Data Science Engineer with a strong background in physics and mathematics, I am thrilled to apply for the PhD position in Artificial Intelligence at the University of Southampton. This opportunity to develop low-cost polysilicon photonic platforms for optoelectronic integration resonates deeply with my research interests and goals.

My previous work on Medical_MambaTS, a linear-time state space model for sub-millisecond bedside inference, has allowed me to appreciate the significance of achieving low latency in various fields. I am excited about the prospect of applying this knowledge to tackle key issues associated with integrating optical and electronic circuits. The development of simple, low-cost laser materials processing procedures to fabricate high-quality polysilicon photonic platforms is a fascinating challenge that aligns perfectly with my skills and expertise.

Furthermore, my experience with PI-DeepONet, a 0D Windkessel Physics-Informed Operator Network using PyTorch Autograd, has taught me the importance of incorporating physical constraints into machine learning models. I believe that this knowledge will be invaluable in developing low-cost polysilicon photonic platforms for optoelectronic integration.

I am confident that my skills and experience make me an ideal candidate for this PhD position. I look forward to contributing to this project and exploring the vast potential of integrated polysilicon photonics.

\closing{\noindent Sincerely}

\signature{\noindent Ismail Aissaoui}

\end{document}