\documentclass[a4paper,12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{geometry}
\geometry{left=1.8cm,right=1.8cm,top=1.3cm,bottom=1.6cm}

\usepackage{lmodern}
\usepackage{xcolor}

\definecolor{titleblue}{RGB}{0,51,140}
\definecolor{TITLEBLUE}{RGB}{0,51,140}

\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    urlcolor=titleblue,
    linkcolor=titleblue,
    citecolor=titleblue,
    pdfborder={0 0 0}
}

\usepackage{titlesec}
\usepackage{enumitem}

\pagestyle{empty}

\titleformat{\section}
  {\color{titleblue}\Large\bfseries\uppercase}{}{0em}{}
  [\color{titleblue}\titlerule]

\titlespacing\section{0pt}{8pt}{4pt}
\setlist[itemize]{leftmargin=*,topsep=2pt,itemsep=1pt}

\begin{document}

\begin{center}
    {\Huge\bfseries\color{titleblue} AISSAOUI Ismail}\\[4pt]
    {\Large AI \& Data Science Engineer}\\[6pt]

    {\normalsize
    Email: \href{mailto:ismail.aissaoui.pro@gmail.com}{ismail.aissaoui.pro@gmail.com} \quad
    Phone: +213 660 70 77 96 \\
    Portfolio: \href{https://ismail-aissaoui.vercel.app}{ismail-aissaoui.vercel.app} \quad
    Location: Chlef, Algeria \\
    LinkedIn: \href{https://linkedin.com/in/aissaoui-ismail-6a77a92a7}{linkedin.com/in/aissaoui-ismail-6a77a92a7} \quad
    GitHub: \href{https://github.com/i-aissaoui}{github.com/i-aissaoui}
    }
\end{center}

%===========================
\section{PROFILE}
AI \& Data Science Engineer specialized in Deep Learning (Transformers, Mamba) and Edge AI. Proven ability to build end-to-end ML pipelines, optimize model inference, and deploy robust AI solutions that translate technical outcomes into business value.

%===========================
\section{SKILLS}
\textbf{Programming}: Python, TypeScript, JavaScript, Java, SQL \\
\textbf{ML / DL}: PyTorch, TensorFlow, Keras, Scikit-learn, Lightning, ONNX \\
\textbf{AI Techniques}: Transformers (BERT, GPT, RAG), GNN, GAN, XGBoost, LSTM \\
\textbf{Optimization}: PSO, Genetic Algorithm, ACO, Simulated Annealing, Bayesian Optimization \\
\textbf{Web \& API}: React, Next.js, FastAPI, Node.js, TailwindCSS \\
\textbf{Data \& MLOps}: MLflow, Airflow, Kubeflow, DVC, Pandas, NumPy \\
\textbf{Databases}: PostgreSQL, MongoDB, MySQL, Neo4j, Cassandra \\
\textbf{Cloud \& DevOps}: Docker, Linux, Git, CI/CD, CUDA, AWS, Grafana 

%===========================
\section{PROFESSIONAL EXPERIENCE}
\textbf{Graduate AI Research Engineer (Intern)} \hfill Jan 2026 -- Jul 2026 \\
Sonatrach (Industrial Surveillance Division) — Algeria \\
Architected an AI-native Digital Twin for real-time monitoring of Gas Turbines.
\begin{itemize}
    \item Built a Physics-Informed Digital Twin (PINN) using \textbf{Mamba-SSM} and \textbf{xLSTM} architectures.
    \item Achieved \textbf{0.04ms edge inference} via hardware-software co-design and C++ JIT optimization.
    \item Engineered custom PINN loss functions to ensure strict thermodynamic consistency.
    \item Developed quantitative indicators for Out-of-Distribution (OOD) anomaly detection.
\end{itemize}

\vspace{8pt}
\textbf{Network Engineering Intern} \hfill Sep 2024 \\
Algérie Télécom RMC Center — Chlef, Algeria

%===========================
\section{EDUCATION}
\textbf{National Higher School of Computer Science (ESI-SBA)} \hfill 2021--2026 \\
Engineering and Master’s Degree in Computer Science \\
Specialization: Artificial Intelligence \& Data Science


%===========================
\section{CERTIFICATIONS}
\textbf{DeepLearning.AI}: Machine Learning Specialization, Deep Learning Specialization, NLP Specialization \\[6pt]
\textbf{ZTM Academy}: PyTorch: Zero to Mastery, TensorFlow Developer

%===========================
% Force projects + languages onto page 2
\newpage

\section{PROJECTS}
\setlength{\parskip}{0pt}

\noindent\textbf{\large Industrial Gas Turbine Digital Twin (Sonatrach)} \hfill \textbf{2026}
\vspace{2pt}
{\small
\begin{itemize}
    \item \textbf{Surrogate Modeling}: Engineered a real-time Physics-Informed Digital Twin using Mamba-SSM and xLSTM.
    \item \textbf{Generative 'What-If'}: Implemented generative scenario forecasting for predictive maintenance.
    \item \textbf{XAI \& RAG}: Integrated Retrieval-Augmented Generation and Explainable AI for transparent anomaly diagnosis.
    \item \textbf{Edge Optimization}: Achieved 0.04ms edge inference via hardware-software co-design and C++ JIT optimization.
\end{itemize}
\textit{Tech: Mamba-SSM, xLSTM, PyTorch, C++ JIT, PINN, RAG, XAI}
}
\vspace{8pt}

\noindent\textbf{\large Cardiovascular Medical Digital Twin} \hfill \textbf{2026}
\vspace{2pt}
{\small
\begin{itemize}
    \item \textbf{Physics-Informed Modeling}: Architected a Digital Twin modeling 1D Hemodynamic Navier-Stokes flows to predict anomalies.
    \item \textbf{Spatio-Temporal Distillation}: Integrated ST-KDFormer to balance high-fidelity physics with computational efficiency.
    \item \textbf{Data Streaming}: Engineered real-time ingestion of physiological data streams using Apache Kafka.
\end{itemize}
\textit{Tech: PyTorch, PINN, ST-KDFormer, Kafka, Fluid Mechanics}
}
\vspace{8pt}

\noindent\textbf{\large Aura — Enterprise AI Trading Platform} \hfill \textbf{2025}
\vspace{2pt}
{\small
\begin{itemize}
    \item \textbf{Hybrid Forecasting}: Built an autonomous trading system combining LSTM networks for time-series predictions.
    \item \textbf{Strategic Decision-Making}: Implemented Deep Q-Learning (Reinforcement Learning) to optimize long-term reward policies.
    \item \textbf{Real-Time Dashboard}: Engineered a high-throughput FastAPI backend with WebSockets and a Next.js interactive UI.
\end{itemize}
\textit{Tech: TensorFlow, PyTorch, FastAPI, Next.js, WebSockets, RL}
}
\vspace{8pt}

\noindent\textbf{\large GNN-based Recruiting System (Career Connect)} \hfill \textbf{2024--2025}
\vspace{2pt}
{\small
\begin{itemize}
    \item \textbf{Relational Learning}: Developed a recommendation engine using Graph Neural Networks (GNN) to map candidate-job relationships.
    \item \textbf{Semantic Embeddings}: Utilized PyTorch Geometric and SBERT for deep semantic text processing.
    \item \textbf{System Architecture}: Deployed via FastAPI and PostgreSQL, significantly outperforming keyword-based heuristics.
\end{itemize}
\textit{Tech: PyTorch Geometric, SBERT, FastAPI, PostgreSQL, GNN}
}
\vspace{12pt}

%===========================
\section{LANGUAGES}
Arabic: Native \quad|\quad French: Fluent \quad|\quad English: Fluent

\end{document}
