Here is the motivation letter in LaTeX format:

\documentclass{letter}

\begin{document}

\opening{\noindent To Whom It May Concern,}

I am writing to express my strong interest in the PhD position "Integrating Quantum and Classical Sensors for Long-Duration Inertial Navigation" at the University of Southampton. As an AI & Data Science Engineer with a passion for innovative solutions, I believe that this project aligns perfectly with my skills and expertise.

My experience in developing a linear-time state space model (Medical_MambaTS) has allowed me to appreciate the importance of low-latency inference in various applications. In the context of inertial navigation, Medical_MambaTS's ability to provide sub-millisecond bedside inference can be adapted to fusion algorithms for real-time navigation corrections. I am excited about the prospect of applying this knowledge to develop robust and efficient fusion algorithms that combine classical inertial sensors with quantum measurements.

Furthermore, my experience in building a Physics-Informed Operator Network (PI_DeepONet) using PyTorch Autograd has provided me with a deep understanding of physical constraints and their impact on system performance. I believe that this expertise can be leveraged to develop accurate models for simulating the behavior of classical inertial sensors and quantum gyroscopes, enabling more effective testing and validation of fusion algorithms.

I am confident that my skills and experience make me an ideal candidate for this project. I look forward to the opportunity to contribute to the development of hybrid quantum-classical navigation systems and explore their applications in GPS-denied environments.

\closing{\noindent Sincerely,}

\end{document}