\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}

\hypersetup{colorlinks=true, urlcolor=blue, linkcolor=black}

\begin{document}
\thispagestyle{empty}

\begin{flushright}
\textbf{Ismail Aissaoui} \\
Email: \href{mailto:i.aissaoui@esi-sba.dz}{i.aissaoui@esi-sba.dz} \\
Phone: +213 660 70 77 96 \\
Portfolio: \href{https://ismail-aissaoui.vercel.app}{ismail-aissaoui.vercel.app}
\end{flushright}

\vspace{1em}

\begin{flushleft}
\textbf{Sophie Eberdold} (UT2J) \\
\textbf{Marcos Didonet del Fabro} (CEA List) \\
UT2J-IRIT-SM@RT
\end{flushleft}

\vspace{1em}
\noindent\textbf{Subject: Application for PhD Position -- Methodology for Engineering Digital Twins (PC3)}
\vspace{1em}

\noindent Dear Sophie Eberdold and Marcos Didonet del Fabro,

\vspace{1em}
\noindent
I am writing to express my profound interest in the PhD position on "Methodology for Engineering Digital Twins," co-supervised at UT2J-IRIT-SM@RT and CEA List. With my robust engineering background in systems architecture, Model-Driven Engineering (MDE), and AI integration, I am highly motivated to tackle the challenge of defining rigorous methodologies for the lifecycle management and federation of digital twins.

\vspace{0.5em}
\noindent
A central challenge in current digital twin engineering is the lack of standardized formalisms to manage their evolution, orchestration, and validation. During my engineering of the "Autonomous Cyber-Shield Platform" and the "Industrial Gas Turbine Digital Twin," I confronted the complexities of integrating heterogeneous models—from purely physical thermodynamic simulations to data-driven AI inference components. To ensure interoperability and maintainability, I employed strict systems engineering principles, creating modular boundaries that allowed each sub-system to evolve independently while still communicating through standardized interfaces. This hands-on experience in architecting complex, multi-layered cyber-physical systems perfectly positions me to develop the methodological frameworks you require. I am eager to research novel model-driven techniques to define clear workflows, ensure traceability, and automate the deployment of digital twins across the Artemis platform.

\vspace{0.5em}
\noindent
Furthermore, my deep technical knowledge enables me to bridge the gap between high-level conceptual modeling and low-level programmatic implementation. I am eager to collaborate closely with the AT3 engineering teams to validate these methodologies on real-world industrial use cases. Please find attached my resume and academic transcripts. I welcome the opportunity to discuss my application further.

\vspace{1.5em}
\noindent
Sincerely, \\[0.5em]
\textbf{Ismail Aissaoui}

\end{document}
