Here is the motivation letter in LaTeX format:

\documentclass{letter}

\address{\noindent Technical University of Munich\\
         Institute for AI and Informatics in Medicine (AIIM)\\
         Location: Munich, Germany}

\signature{\noindent Ismail Aissaoui\\
          AI & Data Science Engineer}

\begin{document}

\opening{}

Dear Felix Busch,

I am writing to express my strong interest in the PhD position in Computer Science at the Institute for AI and Informatics in Medicine (AIIM) at Technical University of Munich. As a highly motivated and experienced AI & Data Science Engineer, I am confident that my skills and research background align perfectly with the requirements of this prestigious program.

During my master's studies, I had the opportunity to work on several projects that showcased my expertise in developing innovative solutions for complex problems. One project that stands out is the "Cardiovascular Medical Digital Twin" where I developed a linear-time state space model called Medical_MambaTS for sub-millisecond bedside inference. This achievement demonstrates my ability to design and implement efficient algorithms, which will be crucial in the development of AI-powered medical informatics systems.

Furthermore, I had the chance to work on a 0D Windkessel Physics-Informed Operator Network using PyTorch Autograd called PI_DeepONet. This project allowed me to apply physical constraints to my models, which is essential in precision oncology where accurate predictions are crucial for effective treatment planning.

I am particularly drawn to this PhD position because of its focus on AI and medical informatics for hepato-pancreato-biliary cancers. My research interests align perfectly with the goals of the project, and I believe that my skills will be highly valuable in achieving the project's objectives.

In conclusion, I am confident that my unique blend of AI and data science expertise makes me an ideal candidate for this PhD position. I look forward to the opportunity to discuss my application and how I can contribute to the xMDT-HPB project at AIIM.

Thank you for considering my application.

Sincerely,

Ismail Aissaoui

\closing{}

\end{document}

Please note that I have only included two achievements, Medical_MambaTS and PI_DeepONet, which I believe map perfectly to the specific requirements of this PhD offer.