\documentclass[a4paper,11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{geometry}

\geometry{left=1.5cm,right=1.5cm,top=1.2cm,bottom=1.2cm}

\usepackage{lmodern}
\usepackage{xcolor}
\definecolor{titleblue}{RGB}{0,51,140}
\definecolor{TITLEBLUE}{RGB}{0,51,140}

\usepackage{hyperref}
\hypersetup{colorlinks=true, urlcolor=titleblue, linkcolor=titleblue}

\usepackage{titlesec}
\usepackage{enumitem}

\pagestyle{empty}

\titleformat{\section}{\color{titleblue}\Large\bfseries\uppercase}{}{0em}{}[\color{titleblue}\titlerule]
\titlespacing\section{0pt}{8pt}{4pt}
\setlist[itemize]{leftmargin=*,topsep=1pt,itemsep=1pt}

\begin{document}

\begin{center}
    {\Huge\bfseries\color{titleblue} AISSAOUI Ismail}\\[4pt]
    {\Large State Engineer in Artificial Intelligence \& Data Science}\\[6pt]
    ismail.aissaoui.pro@gmail.com $|$ +213 660 70 77 96 $|$ Algeria \\
    \href{https://linkedin.com/in/aissaoui-ismail-6a77a92a7}{linkedin.com/in/aissaoui-ismail-6a77a92a7} $|$ \href{https://github.com/i-aissaoui}{github.com/i-aissaoui}
\end{center}

\section{RESEARCH SUMMARY}
State Engineer (ESI-SBA) specializing in \textbf{Physics-Informed Machine Learning (PINN)}, \textbf{Interpretability}, and \textbf{Robustness} for industrial Digital Twins. Expert in integrating physical laws into deep learning architectures (Mamba-SSM/xLSTM) and developing quantitative indicators for model reliability. Proven track record in accelerating physics-based simulations for large-scale energy systems (Sonatrach).

\section{EDUCATION}
\textbf{National School of Computer Science (ESI-SBA, Algeria)} \hfill 2021 -- 2026 \\
\textbf{State Engineer's Degree \& MSc in Artificial Intelligence}

\section{RESEARCH PROJECTS}

\textbf{Physics-Informed Digital Twin — Sonatrach} \hfill 2026 \\
Development of a generative surrogate for gas turbine monitoring.
\begin{itemize}
    \item Implemented custom \textbf{PINN loss functions} to enforce thermodynamic laws.
    \item Developed a dual-track architecture using \textbf{Mamba-SSM} and \textbf{xLSTM}.
    \item Investigated \textbf{Uncertainty Quantification} and reliability metrics for OOD (Out-of-Distribution) detection in industrial surrogates.
    \item Optimized for resource-constrained edge devices with \textbf{0.04ms} latency.
\end{itemize}

\textbf{Industrial Safety \& CV Monitoring (YOLOv8)} \hfill 2025 \\
Computerized image processing system for safety equipment detection and tracking.
\textit{Key skill: Computerized Image Processing \& Object Tracking.}

\textbf{Recognizini — Real-Time Face Recognition} \hfill 2025 \\
High-speed vision system with active learning and incremental embeddings.

\textbf{Geo-RAG — Semantic Knowledge Retrieval} \hfill 2025 \\
Knowledge extraction from multi-source industrial and geospatial data.

\textbf{Career Connect — Structural GNN Intelligence} \hfill 2024 -- 2025 \\
Relational modeling of complex systems via Graph Neural Networks.

\section{TECHNICAL SKILLS}
\begin{itemize}
    \item \textbf{Physics-Informed AI}: PINN (Loss design), Koopman Theory, Physics-Aware Loss.
    \item \textbf{Computer Vision}: YOLOv8, OpenCV, Image Segmentation, Active Learning.
    \item \textbf{Sequence Modeling}: Mamba-SSM, xLSTM, Informer, TCN.
    \item \textbf{Engineering}: PyTorch, C++, Docker, MLflow, CUDA, Linux, Git.
\end{itemize}

\section{LANGUAGES}
Arabic (Native), English (Advanced - Professional Research Level), French (Fluent).

\end{document}
