\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}

\hypersetup{colorlinks=true, urlcolor=blue, linkcolor=black}

\begin{document}
\thispagestyle{empty}

\begin{flushright}
\textbf{Ismail Aissaoui} \\
Email: \href{mailto:i.aissaoui@esi-sba.dz}{i.aissaoui@esi-sba.dz} \\
Phone: +213 660 70 77 96 \\
Portfolio: \href{https://ismail-aissaoui.vercel.app}{ismail-aissaoui.vercel.app}
\end{flushright}

\vspace{1em}

\begin{flushleft}
\textbf{Arnaud Blouin \& Benoit Combemale} (Univ Rennes, IRISA, Inria) \\
\textbf{Romain Rouvoy} (University of Lille)
\end{flushleft}

\vspace{1em}
\noindent\textbf{Subject: Application for PhD Position -- Modeling the construction of digital twins (PC3)}
\vspace{1em}

\noindent Dear Arnaud Blouin, Benoit Combemale, and Romain Rouvoy,

\vspace{1em}
\noindent
I am applying with great enthusiasm for the PC3 PhD position focused on "Modeling the construction of digital twins." Given my deep engineering background in systems architecture, model-driven engineering (MDE), and continuous deployment, I am highly motivated to define the formal methodologies required to orchestrate the lifecycle of complex, multi-layered digital twin systems.

\vspace{0.5em}
\noindent
The industrial deployment of a Digital Twin is rarely a single, monolithic event; it is a continuous process of integration, validation, and updating. During my work engineering the "Autonomous Cyber-Shield Platform," I confronted the complexities of continuous integration for cyber-physical models. I architected a deployment pipeline that synchronized updates between a Python-based Reinforcement Learning agent and a live Next.js visualization dashboard, all without disrupting the core system runtime. This required defining strict configuration models and deployment semantics. I am eager to formally abstract these practices into generalized modeling languages. My goal is to research and formalize the construction processes---defining exactly how simulation models, data pipelines, and UI components are assembled and deployed dynamically across the cloud-to-edge continuum.

\vspace{0.5em}
\noindent
Furthermore, my expertise in building highly modular architectures positions me perfectly to contribute to the Artemis framework. I am excited to collaborate with the DiverSE and Spirals teams to build the robust software engineering tooling needed to turn digital twin construction from an ad-hoc craft into an automated, mathematically sound discipline. Please find attached my resume and academic transcripts. I welcome the opportunity to discuss my application further.

\vspace{1.5em}
\noindent
Sincerely, \\[0.5em]
\textbf{Ismail Aissaoui}

\end{document}
