\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}

\hypersetup{colorlinks=true, urlcolor=blue, linkcolor=black}

\begin{document}
\thispagestyle{empty}

\begin{flushright}
\textbf{Ismail Aissaoui} \\
Email: \href{mailto:i.aissaoui@esi-sba.dz}{i.aissaoui@esi-sba.dz} \\
Phone: +213 660 70 77 96 \\
Portfolio: \href{https://ismail-aissaoui.vercel.app}{ismail-aissaoui.vercel.app}
\end{flushright}

\vspace{1em}

\begin{flushleft}
\textbf{Pr. Brahim Hamid} (IRIT Laboratory, UT2J) \\
\textbf{Dr. Marcos Didonet Del Fabro} (CEA List)
\end{flushleft}

\vspace{1em}
\noindent\textbf{Subject: Application for PhD Position -- AI-Assisted Security Engineering for Digital Twins (PC3)}
\vspace{1em}

\noindent Dear Pr. Hamid and Dr. Didonet Del Fabro,

\vspace{1em}
\noindent
I am writing to express my profound interest in the PhD position on "AI-Assisted Model-Driven Security Engineering for Digital Twins." With my robust engineering background in Artificial Intelligence, Graph Neural Networks (GNNs), and automated cybersecurity architectures, I am highly motivated to tackle the challenge of developing an automated round-trip framework for the Asset Administration Shell (AAS) specification.

\vspace{0.5em}
\noindent
In my engineering of the "Autonomous Cyber-Shield Platform," I confronted the complexities of closing the loop between threat mitigation and system architecture. I designed a highly deployable architecture that integrated a Reinforcement Learning penetration tester directly against an autonomous firewall defender (Blue AI). By utilizing Adversarial Co-Evolution, I modeled complex security environments where the system autonomously learned and fed security rules back into the baseline architecture. This hands-on experience in AI-driven cybersecurity perfectly aligns with your objective to integrate AI assistance into the modeling of Digital Twins. I am fully prepared to extend these capabilities into the AAS specification, ensuring that model-driven engineering processes can seamlessly adapt to dynamic security threats in real-time.

\vspace{0.5em}
\noindent
Furthermore, my deep knowledge of Model-Driven Engineering positions me to design the necessary formalisms to bridge the gap between design-time security and run-time monitoring. I am eager to leverage my skills to develop the required Proof of Concept framework and contribute meaningfully to the EDT case studies. Please find attached my resume and academic transcripts. I look forward to discussing how my expertise can accelerate the development of an automated security framework within your teams.

\vspace{1.5em}
\noindent
Sincerely, \\[0.5em]
\textbf{Ismail Aissaoui}

\end{document}
