Here is the motivation letter in LaTeX format:

\documentclass{letter}
\begin{document}

\opening{Dear PhD Admissions Committee,}

I am writing to express my strong interest in pursuing a PhD in Decision Making for Complex Systems at the University of Cambridge. With my background in AI and Data Science Engineering, I am confident that this program will provide me with the ideal platform to develop my research skills and contribute meaningfully to the field.

As an engineer, I have had the opportunity to work on various projects that involve decision-making in complex systems. One project that stands out is the development of Medical_MambaTS, a linear-time state space model for sub-millisecond bedside inference. This project allowed me to work with medical professionals to develop a predictive model that can make decisions in real-time, which aligns perfectly with the focus on decision-making in complex systems.

Another project that I am proud of is PI_DeepONet, a 0D Windkessel Physics-Informed Operator Network using PyTorch Autograd. This project allowed me to work with physical constraints and develop a model that can make predictions based on physical laws. The use of physics-informed neural networks (PINNs) in this project has shown great promise in predicting complex systems, which is also the focus of this PhD program.

I am excited about the opportunity to join the University of Cambridge's Department of Computer Science and Technology and contribute to the research in decision making for complex systems. I am confident that my skills and experience make me a strong candidate for this program.

\closing{Sincerely,}
\signature{Ismail Aissaoui}

\end{document}