Here is a motivation letter for the PhD position:

\documentclass{letter}

\begin{document}
\opening{June 14, 2026}

Delft University of Technology,
Delft, Netherlands.

Dear Dr. Jing Sun,

I am excited to apply for the fully funded PhD position in Scientific Machine Learning (SciML) at Delft University of Technology, as advertised on [Original Link](https://www.phdscanner.com/opportunities/phd-vacancies-delft-university-of-technology-netherlands-phd-position-scientific-machine-learning-toward-scientific-foundation-models-a42e35d2-c94d-409b-804a-b8411439be5f). As a highly motivated and detail-oriented AI & Data Science Engineer, I am confident that my skills and experience make me an ideal candidate for this project.

My research background is deeply rooted in SciML, with a strong focus on developing foundation models for complex systems modeling. During my Master's thesis, I worked on the "Cardiovascular Medical Digital Twin" project, where I developed several innovative solutions that perfectly align with the requirements of this PhD position. Specifically, I would like to highlight two achievements that demonstrate my expertise in SciML.

Firstly, I developed a linear-time state space model called Medical_MambaTS, which enables sub-millisecond bedside inference for critical applications such as cardiovascular disease diagnosis and treatment planning. This achievement showcases my ability to design and implement efficient algorithms for complex systems modeling, which is crucial for the development of foundation models in this project.

Secondly, I designed a 0D Windkessel Physics-Informed Operator Network called PI_DeepONet using PyTorch Autograd, which combines physical constraints with machine learning techniques. This achievement demonstrates my understanding of physics-informed neural networks and hybrid physics-ML approaches, both of which are essential for developing foundation models that integrate scientific knowledge and data-driven machine learning techniques.

In addition to these achievements, I have also worked on missingness-aware gate design for handling sensor dropouts and missing data in real-world applications. This experience has taught me the importance of robustness and adaptability in SciML models, which is a key aspect of this PhD project.

I am confident that my skills and experience make me an excellent fit for this PhD position. I am excited about the opportunity to contribute to the development of foundation models for complex systems modeling and explore modern SciML methods such as physics-informed neural networks and hybrid physics-ML approaches.

Thank you for considering my application. I look forward to discussing my qualifications further.

Sincerely,

Ismail Aissaoui

\closing{}
\end{document}