\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}

\hypersetup{colorlinks=true, urlcolor=blue, linkcolor=black}

\begin{document}
\thispagestyle{empty}

\begin{flushright}
\textbf{Ismail Aissaoui} \\
Email: \href{mailto:i.aissaoui@esi-sba.dz}{i.aissaoui@esi-sba.dz} \\
Phone: +213 660 70 77 96 \\
Portfolio: \href{https://ismail-aissaoui.vercel.app}{ismail-aissaoui.vercel.app}
\end{flushright}

\vspace{1em}

\begin{flushleft}
\textbf{Hiring Committee} \\
Earth Observation EDT Team
\end{flushleft}

\vspace{1em}
\noindent\textbf{Subject: Application for PhD Position -- Large Language Models for Earth Observation Digital Twins}
\vspace{1em}

\noindent Dear Hiring Committee,

\vspace{1em}
\noindent
I am applying for the PhD position on "Large Language Models for Earth Observation Digital Twins" with great enthusiasm. With a strong engineering background in Artificial Intelligence, distributed computing, and complex system modeling, I am highly motivated to contribute to the Artemis framework and tackle the unique challenges presented by this project.

\vspace{0.5em}
\noindent
Integrating Large Language Models into vast, complex geospatial datasets represents the cutting edge of digital twin accessibility. My background in AI architectures, specifically in sequence modeling and visual data representation, positions me well to bridge the gap between natural language queries and massive earth observation data. I am eager to explore how LLMs can democratize access to geographical digital twins and automate complex analytical tasks.

\vspace{0.5em}
\noindent
I am particularly drawn to this position because it bridges rigorous research with practical industrial challenges within the EDT program. Please find attached my resume and academic transcripts, which detail my technical competencies and engineering background. I welcome the opportunity to discuss my application further.

\vspace{1.5em}
\noindent
Sincerely, \\[0.5em]
\textbf{Ismail Aissaoui}

\end{document}