\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{geometry}
\usepackage{xcolor}
\usepackage{hyperref}

\geometry{margin=1in}
\definecolor{lorraine_blue}{RGB}{0, 75, 142}

\begin{document}

\noindent \textbf{Ismail AISSAOUI} \\
AI \& Data Science Engineer \\
Email: ismail.aissaoui.pro@gmail.com \\
Phone: +213 660 70 77 96 \\
Location: Algeria \\
GitHub: \href{https://github.com/i-aissaoui}{github.com/i-aissaoui}

\bigskip

\begin{flushright}
    To Professor Enrique Espinosa \& Professor Sabeur Aridhi \\
    \textbf{Université de Lorraine} \\
    CRM2 / LORIA \\
    Nancy, France \\
    \medskip
    May 11, 2026
\end{flushright}

\bigskip

\noindent \textbf{Subject: Application for PhD Position: Prediction of Molecular Assembly in APIs using AI-Machine Learning}

\bigskip

\noindent Dear Professor Espinosa, Professor Aridhi, and Dr. Aubert,

\medskip

I am writing to formally submit my application for the PhD position focused on predicting molecular assembly in pharmaceutical APIs through AI and Machine Learning. As an AI Engineer from ESI-SBA with a deep specialization in **Physics-Informed Neural Networks (PINNs)** and **Graph Machine Learning**, I am particularly motivated by the challenge of bridging quantum data with 3D molecular organization.

The interdisciplinary nature of this project, combining the crystallographic expertise of **CRM2** with the AI excellence of **LORIA**, represents my ideal research environment. My profile aligns with the core requirements of the thesis in several key areas:

\begin{itemize}
    \item \textbf{Physics-AI Synergy}: In my state engineering thesis at **Sonatrach**, I developed a **Generative Digital Twin** for gas turbines. My research focused on using **PINNs** to embed physical laws directly into the learning process. This methodology is directly transposable to your objective of learning informative representations from **quantum data** (atomic charges, energies); I understand how to ensure that AI predictions respect the underlying physical/chemical "rules" of the system.
    \item \textbf{Structural \& Sequential Modeling}: Predicting molecular assembly is a multi-dimensional structural challenge. My expertise in **Graph Neural Networks (GNNs)** (used for fraud detection and recruitment platforms) and advanced sequential architectures like **Mamba-SSM** and **xLSTM** provides me with the tools to model complex inter-atomic dependencies and the dynamics of self-assembly.
    \item \textbf{Handling High-Fidelity Data}: I have extensive experience in building robust ML pipelines for massive scientific datasets (like the 5.2M point N-CMAPSS). I am proficient in **PyTorch** and **Scikit-learn**, and I am eager to apply these skills to your database of 455,000 entries from DFT calculations.
\end{itemize}

Beyond the technical fit, I am highly interested in **Crystal Engineering** and the phenomenon of **polymorphism**. While my background is in industrial AI, I have always been driven by the "Scientist-in-the-loop" philosophy, where AI serves to accelerate discovery in the physical sciences. I am a fast learner and look forward to acquiring deeper knowledge in quantum chemistry under your guidance.

I am confident that my "model-centric" engineering perspective, combined with my rigorous training at ESI-SBA, will allow me to contribute meaningfully to the project's goal of anticipating 3D assemblies of pharmaceutical principles.

Thank you for your time and consideration. I would be honored to discuss my potential contributions during an interview.

\bigskip

\noindent Sincerely,

\bigskip

\noindent Ismail AISSAOUI

\end{document}
