\documentclass[a4paper,11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{geometry}
\geometry{left=1.8cm,right=1.8cm,top=1.3cm,bottom=1.6cm}

\usepackage{lmodern}
\usepackage{xcolor}
\definecolor{titleblue}{RGB}{0,51,140}

\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    urlcolor=titleblue,
    linkcolor=titleblue,
}

\usepackage{titlesec}
\usepackage{enumitem}

\pagestyle{empty}

\titleformat{\section}
  {\color{titleblue}\Large\bfseries\uppercase}{}{0em}{}
  [\color{titleblue}\titlerule]

\titlespacing\section{0pt}{8pt}{4pt}
\setlist[itemize]{leftmargin=*,topsep=2pt,itemsep=1pt}

\begin{document}

\begin{center}
    {\Huge\bfseries\color{titleblue} Ismail AISSAOUI}\\[4pt]
    {\Large AI \& Data Science Engineer}\\[6pt]
    Email: ismail.aissaoui.pro@gmail.com \quad Phone: +213 660 70 77 96 \\
    Portfolio: \href{https://ismail-aissaoui.vercel.app}{ismail-aissaoui.vercel.app} \quad Location: Algeria \\
    LinkedIn: \href{https://linkedin.com/in/aissaoui-ismail-6a77a92a7}{linkedin.com/in/aissaoui-ismail-6a77a92a7}
\end{center}

\section{SUMMARY}
AI Engineer specializing in **Scientific Machine Learning (SciML)** and **Physics-Informed Neural Networks (PINNs)**. Experienced in developing generative surrogates for complex physical systems, multi-step sequential dynamics (Mamba-SSM/xLSTM), and structural modeling via GNNs. Committed to bridging the gap between deep learning and physical/chemical sciences to solve foundational challenges in molecular assembly and property prediction.

\section{EDUCATION}
\textbf{National Higher School of Computer Science (ESI-SBA)} \hfill 2021--2026 \\
Engineering and Master’s Degree in Computer Science \\
Specialization: **Artificial Intelligence \& Informatics** \\
*Key Coursework: Deep Learning, Graph Machine Learning, Metaheuristic Optimization, Scientific Computing.*

\section{TECHNICAL EXPERTISE}
\textbf{Machine Learning}: PyTorch, TensorFlow, Scikit-learn, Lightning, GNN (PyTorch Geometric), ViT. \\
**Physics-AI**: Physics-Informed Neural Networks (PINNs), PINN-surrogates, Hybrid Modeling. \\
**Sequential Dynamics**: Mamba-SSM, xLSTM, Temporal Convolutional Networks (TCN). \\
**Optimization**: PSO, Genetic Algorithms, Bayesian Optimization, Optuna. \\
**Deployment**: FastAPI, Docker, Edge AI (0.04ms inference), CUDA, Linux.

\section{RESEARCH \& THESIS EXPERIENCE}
\textbf{State Engineering Thesis (Sonatrach)} \hfill Feb 2026 -- July 2026 \\
\textit{Generative Digital Twin for GE LM2500 Gas Turbines}
\begin{itemize}
    \item Developed a **Physics-Informed Digital Twin** capable of predicting high-fidelity thermodynamic states.
    \item Hybridized **PINNs** with sequential architectures (**Mamba-SSM** and **xLSTM**) to capture non-linear temporal dependencies while maintaining physical consistency.
    \item Handled a **5.2M point dataset (N-CMAPSS)**, optimizing data pipelines for multi-sensor telemetry.
    \item Achieved **0.04ms latency** on edge devices through model distillation and JIT compilation.
\end{itemize}

\section{SELECTED PROJECTS}
\textbf{Aura — Enterprise AI Trading System (LSTM + DQN)} \hfill 2025 \\
Automated platform using reinforcement learning to optimize execution policies under reward maximization.

\textbf{Elliptic++ — GNN for Fraud Detection} \hfill 2025 \\
Graph-based classification of illicit nodes in the Bitcoin network using relational learning and node embeddings.

\textbf{Career Connect — AI HR Platform (GNN + RAG)} \hfill 2024 \\
Matching engine using graph embeddings and Google Gemini for deep semantic analysis of professional profiles.

\textbf{Advanced NLP Optimization} \hfill 2025 \\
Benchmarked PSO vs. Genetic Algorithms for hyperparameter tuning of Transformer architectures.

\section{LANGUAGES}
Arabic: Native \quad|\quad French: Fluent (C1/C2) \quad|\quad English: Fluent (C1/C2)

\end{document}
