\documentclass[11pt]{letter}

\address{\begin{tabular}{@{}c}
Ismail Aissaoui \\
123 Main St, Anytown, USA 12345
\end{tabular}}
\signature{\begin{tabular}{@{}l}
Ismail Aissaoui\\
Email: [your email]
\end{tabular}}

\opening{Dear Admissions Committee}

University of Southampton, a world-renowned institution in the field of quantum computing and computational fluid dynamics, I am excited to apply for the PhD position in Quantum Computational Fluid Dynamics.

As an AI & Data Science Engineer with a strong background in physics, mathematics, and engineering, I am confident that my skills and expertise align perfectly with the requirements of this project. Specifically, my experience in developing a linear-time state space model for sub-millisecond bedside inference using Medical_MambaTS resonates well with the requirement of implementing quantum variational algorithms in quantum computers.

In my previous project, Cardiovascular Medical Digital Twin, I utilized PyTorch Autograd to develop a 0D Windkessel Physics-Informed Operator Network (PI-DeepONet) that effectively modeled physical constraints on cardiac flow. This experience has equipped me with the ability to bridge fundamental physics with quantum algorithmic innovation for next-generation fluid simulation.

I am eager to bring my skills and passion to the University of Southampton, where I can contribute to the exciting project exploring the intersection between quantum computing and computational fluid dynamics. The prospect of working on quantum algorithms for fluid simulation and implementing them in quantum computers excites me.

In conclusion, I believe that my unique blend of AI & Data Science expertise, combined with my passion for quantum computing and fluid dynamics, make me an ideal candidate for this PhD position. I look forward to the opportunity to discuss my application further.

Sincerely,

Ismail Aissaoui

\closing{}
\end{letter}