Here is the motivation letter in LaTeX format:

\documentclass[12pt]{letter}

\address{Your Address}
{\textit{Ismail Aissaoui}}
{\textit{AI & Data Science Engineer}}

\date{}
\opening{}

Dear Emilie Chouzenoux,

I am writing to express my strong interest in the PhD position at Inria, Paris, France, focusing on developing an open-source model for abdominal 3D CT imaging in oncology. As a highly motivated and accomplished AI and Data Science Engineer, I am confident that my skills and expertise make me an ideal candidate for this exciting opportunity.

My recent work on Medical_MambaTS, a linear-time state space model for sub-millisecond bedside inference, has allowed me to develop a deep understanding of the importance of low-latency processing in medical imaging. In particular, the ability to process data in real-time is crucial in oncology, where timely diagnosis and treatment are critical factors in patient outcomes. I believe that my experience with Medical_MambaTS can be leveraged to develop an open-source model for abdominal 3D CT imaging that meets the high standards required in this field.

Furthermore, my work on PI_DeepONet, a 0D Windkessel Physics-Informed Operator Network using PyTorch Autograd, has given me a strong foundation in physical constraints and their application to medical imaging. I am excited about the prospect of applying these skills to develop an open-source model for abdominal CT imaging that takes into account the complex physical processes involved.

I am confident that my expertise in AI and Data Science, combined with my passion for medical imaging and oncology, make me a strong candidate for this PhD position. I look forward to discussing my application and qualifications further.

Sincerely,

{\textit{Ismail Aissaoui}}

\closing{}
\enddocument