\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}

\hypersetup{colorlinks=true, urlcolor=blue, linkcolor=black}

\begin{document}
\thispagestyle{empty}

\begin{flushright}
\textbf{Ismail Aissaoui} \\
Email: \href{mailto:i.aissaoui@esi-sba.dz}{i.aissaoui@esi-sba.dz} \\
Phone: +213 660 70 77 96 \\
Portfolio: \href{https://ismail-aissaoui.vercel.app}{ismail-aissaoui.vercel.app}
\end{flushright}

\vspace{1em}

\begin{flushleft}
\textbf{Technical Leadership Committee} \\
EDT Program
\end{flushleft}

\vspace{1em}
\noindent\textbf{Subject: Application for PhD Position -- Technical Lead – Digital Twin Platform}
\vspace{1em}

\noindent Dear Technical Leadership Committee,

\vspace{1em}
\noindent
I am applying for the PhD position on "Technical Lead – Digital Twin Platform" with great enthusiasm. With a strong engineering background in Artificial Intelligence, distributed computing, and complex system modeling, I am highly motivated to contribute to the Artemis framework and tackle the unique challenges presented by this project.

\vspace{0.5em}
\noindent
As a seasoned software engineer with extensive experience architecting full-stack cloud-native applications and Edge-AI deployments, I am highly prepared for this leadership role. My portfolio demonstrates my ability to design scalable Next.js interfaces, manage real-time InfluxDB telemetry, and orchestrate complex Python-based AI backends. I am eager to drive the technical vision for the Artemis platform, ensuring seamless integration of interdisciplinary contributions across the national EDT framework.

\vspace{0.5em}
\noindent
I am particularly drawn to this position because it bridges rigorous research with practical industrial challenges within the EDT program. Please find attached my resume and academic transcripts, which detail my technical competencies and engineering background. I welcome the opportunity to discuss my application further.

\vspace{1.5em}
\noindent
Sincerely, \\[0.5em]
\textbf{Ismail Aissaoui}

\end{document}