\documentclass{letter}
\begin{document}

\opening{Dear PhD Admissions Committee,}

I am excited to apply for the PhD position in Quantum Reservoir Computing via Nano-Opto-Electro-Mechanical (NOEM) coupled quantum oscillators at the University of Southampton. Located in Southampton, United Kingdom, this esteemed institution has a strong reputation for fostering innovation and excellence.

As an AI & Data Science Engineer with a passion for applying mathematical models to real-world problems, I am particularly drawn to this project's focus on developing novel hardware for quantum neural networks. My research experience in computer science, physics, and electronic engineering has equipped me with a solid foundation to tackle the challenges of this project.

One achievement that stands out as highly relevant is my development of Medical_MambaTS, a linear-time state space model capable of generating sub-millisecond bedside inference for cardiovascular medical applications. This expertise in modeling complex systems can be applied to the NOEM coupled oscillators, enabling the development of novel models for quantum reservoir computing hardware.

Another achievement that aligns perfectly with this project is PI_DeepONet, a 0D Windkessel Physics-Informed Operator Network using PyTorch Autograd. This work demonstrated my ability to leverage physical constraints and mathematical modeling to tackle complex problems. In the context of this project, I envision applying similar principles to develop device fabrication routes for NOEM coupled oscillators.

\closing{Sincerely,}
Ismail Aissaoui

\enddocument