Here is the motivation letter:

\documentclass[11pt]{letter}

\begin{document}

\opening{\vspace*{\baselineskip}\noindent Dear Admissions Committee,}

I am writing to express my strong interest in pursuing a PhD as a Research Associate / PhD Student in Information Theory of Sensing and Coordination at the Technical University of Munich (TUM) in Munich, Germany. My name is Ismail Aissaoui, and I am an AI & Data Science Engineer with a passion for developing resilient communication systems.

As a holder of a master's degree in Engineering, I have acquired a solid foundation in Information Theory, which aligns well with the requirements of this PhD program. Throughout my academic and professional journey, I have been fascinated by the potential of AI to revolutionize various fields, including sensing and coordination. My research experience has equipped me with strong skills in Information Theory, and I am eager to leverage these skills to contribute to the development of resilient communication systems.

One achievement that resonates particularly well with this PhD program is my work on Medical_MambaTS, a linear-time state space model for sub-millisecond bedside inference. This project highlights my ability to develop fast and efficient algorithms, which is critical in the context of sensing and coordination. The real-time processing capabilities of Medical_MambaTS enable devices to generate a common approximation of the source within a defined quality level, ensuring that the behavior of devices can be explained and predicted.

I am confident that my academic background, research experience, and achievements make me an excellent candidate for this PhD program. I am excited about the opportunity to join the TUM community and contribute to the development of innovative solutions in Information Theory of Sensing and Coordination.

\closing{\vspace*{\baselineskip}\noindent Sincerely,}

\end{document}