\documentclass[11pt, a4paper]{letter}
\usepackage[utf8]{inputenc}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}

\begin{document}
\begin{letter}{Junior Research Group in AI in Biomedical Imaging \\ Luxembourg Centre for Systems Biomedicine (LCSB) \\ University of Luxembourg}
\opening{Dear Members of the Selection Committee,}

I am writing to express my strong interest in the Doctoral Researcher position focusing on AI and Machine Learning for Biomedical Imaging. As an AI \& Data Science Engineer with extensive academic experience in translating complex medical data into predictive deep learning architectures, I am highly motivated to contribute to your research on neurodegenerative diseases.

Throughout my engineering theses, I have focused heavily on building robust and trustworthy AI models for clinical applications. For my Master's thesis on the "Cardiovascular Medical Digital Twin," I worked extensively with complex medical parameters and multimodal inputs to predict critical health outcomes. I engineered Medical\_MambaTS, a linear-time state-space model that processes high-dimensional, irregular clinical data without the quadratic bottleneck of standard transformers. More importantly, I developed PI-DeepONet, a Physics-Informed Operator Network that maps the strict mathematical constraints of hemodynamics directly into the neural architecture.

This experience of embedding structural deterministic rules into "black-box" neural networks via PyTorch Autograd is directly applicable to the challenges of biomedical image computing. When developing state-of-the-art methods for image segmentation and detection—especially for complex neurodegenerative tracking—ensuring that the AI model is trustworthy and robust against data sparsity is paramount. I am highly proficient in Python, PyTorch, and navigating complex High-Performance Computing (HPC) environments for model training.

I am eager to transition my background in medical digital twins and continuous-time modeling toward computer vision and pattern recognition at the LCSB. Please find attached my CV and academic transcripts for your review.

I look forward to the possibility of discussing how my skills align with your research goals.

\closing{Sincerely, \\ Ismail Aissaoui \\ \href{https://ismail-aissaoui.vercel.app}{https://ismail-aissaoui.vercel.app}}
\end{letter}
\end{document}