\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{titlesec}

\geometry{margin=1in}
\definecolor{tumblue}{RGB}{0,101,189}

\hypersetup{
    colorlinks=true,
    linkcolor=tumblue,
    urlcolor=tumblue,
    pdftitle={Cover Letter - Ismail AISSAOUI},
}

\begin{document}

\noindent \textbf{Ismail AISSAOUI} \\
State Engineer in Artificial Intelligence (ESI-SBA) \\
Email: ismail.aissaoui@example.com \\
Phone: [Your Phone Number] \\
LinkedIn: [Your Link]

\bigskip

\begin{flushright}
    Professor Stephan Günnemann \\
    \textbf{Technical University of Munich (TUM)} \\
    Data Analytics and Machine Learning Group \\
    Munich, Germany \\
    \medskip
    May 5, 2026
\end{flushright}

\bigskip

\noindent \textbf{Subject: Application for Doctoral Research - Robust Sequential & Graph ML}

\bigskip

Dear Professor Günnemann,

I am writing to formally submit my application for a doctoral position within the Data Analytics and Machine Learning group at the Technical University of Munich. As an AI Engineer specializing in advanced neural architectures for complex systems, I have long admired your work on robust graph learning and uncertainty estimation, and I am eager to contribute to your group's research.

In my current role at **Sonatrach**, I am leading the development of a **Generative Digital Twin** for gas turbine health monitoring. This project has required me to move beyond standard deep learning paradigms to ensure model robustness in high-stakes industrial environments. I have been specifically investigating **State Space Models (Mamba-SSM)** and **xLSTM** as scalable alternatives to Transformers, finding that their ability to handle long-range dependencies with linear complexity is critical for real-time industrial sequences.

I am particularly interested in your research on the robustness of **Graph Neural Networks (GNNs)**. My background includes applying GNNs to model structural dependencies and sensor networks, and I am keen to explore how these graph-based models can be combined with SSMs to create "Robust Spatial-Temporal" architectures. Furthermore, my experience with **Physics-Informed Neural Networks (PINNs)** has given me a unique perspective on how to use domain-specific constraints to regularize latent representations, a topic that I believe aligns with your interest in theoretically sound machine learning.

TUM is my top choice for a PhD due to its reputation as a leader in computation and information technology. I am a self-driven researcher with a strong background in Python and PyTorch, and I am ready to commit to the rigorous academic standards of your laboratory.

I have attached my academic transcripts, my CV (from H+ recognized ESI-SBA), and a research proposal for your review. I would be honored to discuss how my technical skills and passion for robust ML can contribute to your group.

Thank you for your time and consideration.

Sincerely,

\bigskip

\noindent Ismail AISSAOUI

\end{document}
