\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}

\hypersetup{colorlinks=true, urlcolor=blue, linkcolor=black}

\begin{document}
\thispagestyle{empty}

\begin{flushright}
\textbf{Ismail Aissaoui} \\
Email: \href{mailto:i.aissaoui@esi-sba.dz}{i.aissaoui@esi-sba.dz} \\
Phone: +213 660 70 77 96 \\
Portfolio: \href{https://ismail-aissaoui.vercel.app}{ismail-aissaoui.vercel.app}
\end{flushright}

\vspace{1em}

\begin{flushleft}
\textbf{Jérôme David \& Cassia Trojahn} (MOEX Team) \\
\textbf{Sophie Ebersold} (IRIT)
\end{flushleft}

\vspace{1em}
\noindent\textbf{Subject: Application for PhD Position -- Interconnection of digital twin knowledge}
\vspace{1em}

\noindent Dear Jérôme David, Cassia Trojahn, and Sophie Ebersold,

\vspace{1em}
\noindent
I am applying for the PhD position on "Interconnection of digital twin knowledge" with great enthusiasm. With a strong engineering background in Artificial Intelligence, distributed computing, and complex system modeling, I am highly motivated to contribute to the Artemis framework and tackle the unique challenges presented by this project.

\vspace{0.5em}
\noindent
My foundation in knowledge engineering and inductive Graph Neural Networks perfectly aligns with the goal of interconnecting digital twin knowledge graphs. In my prior projects, mapping dynamic network topologies into semantically rich graph structures was critical for predictive analytics. I am eager to leverage this experience to design ontology alignment methodologies that can seamlessly interconnect diverse digital twin data streams.

\vspace{0.5em}
\noindent
I am particularly drawn to this position because it bridges rigorous research with practical industrial challenges within the EDT program. Please find attached my resume and academic transcripts, which detail my technical competencies and engineering background. I welcome the opportunity to discuss my application further.

\vspace{1.5em}
\noindent
Sincerely, \\[0.5em]
\textbf{Ismail Aissaoui}

\end{document}