\documentclass{letter}

\begin{document}

\opening{Dear PhD Admissions Committee,}

I am writing to express my strong interest in pursuing a PhD in Quantum Computing and Optimisation for Large-Scale Energy System Planning under Uncertainty at the University of Southampton. As a data science engineer with a passion for applying AI to complex problems, I believe that this project aligns perfectly with my skills and interests.

My recent work on Medical_MambaTS has granted me a unique perspective on the importance of low-latency state space models in high-stakes applications. In the context of energy system planning under uncertainty, I envision MambaTS as a critical component for rapid bedside inference in power grid optimization. By leveraging linear-time state space models, we can develop scalable algorithms that account for uncertainty in renewable generation.

In addition to my experience with Medical_MambaTS, I have also worked on PI_DeepONet, which has given me insight into the importance of physical constraints in optimisation problems. In this project, I believe that applying PI-DeepONet's 0D Windkessel Physics-Informed Operator Network would allow us to develop more accurate and robust algorithms for large-scale energy system planning.

I am excited about the opportunity to join the University of Southampton as a PhD student and contribute my skills and experience to this innovative project. Thank you for considering my application.

\closing{Sincerely,}

Ismaïl Aïssaoûi

\end{document}