Here is the motivation letter:

\documentclass{letter}

\begin{document}

\opening{\noindent To Whom It May Concern,}

I am writing to express my strong interest in the PhD position "Defending deployed AI models: manipulation as a countermeasure" at Inria, Paris, France. As an AI & Data Science Engineer with a passion for developing robust and secure AI solutions, I believe this opportunity aligns perfectly with my research interests and skills.

My background in AI and data science has equipped me with the ability to develop innovative AI models, such as Medical_MambaTS, which leverages linear-time state space modeling for sub-millisecond bedside inference. This achievement showcases my expertise in developing high-performance AI models that can be deployed in real-world applications. I am excited about the prospect of applying this knowledge to defend deployed AI models against manipulation attacks.

Furthermore, my experience with physics-informed neural networks (PINNs) through PI_DeepONet has given me a deep understanding of the importance of incorporating physical constraints into AI model development. This expertise can be leveraged to develop AI models that are more robust to manipulation attacks by incorporating domain-specific knowledge and physical constraints. I am confident that my skills in PINNs and AI model development will enable me to make significant contributions to this research area.

I am particularly drawn to this PhD position because of its focus on AI security, which is a critical aspect of ensuring the reliability and trustworthiness of deployed AI models. As an engineer with strong math and Python skills, I am confident that I can contribute meaningfully to the development of algorithms and experimentation in this field.

In closing, I would like to express my sincere interest in pursuing a PhD at Inria under this position. Thank you for considering my application.

\closing{\noindent Sincerely,}

Ismail Aissaoui

\end{document}