\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}

\hypersetup{colorlinks=true, urlcolor=blue, linkcolor=black}

\begin{document}
\thispagestyle{empty}

\begin{flushright}
\textbf{Ismail Aissaoui} \\
Email: \href{mailto:i.aissaoui@esi-sba.dz}{i.aissaoui@esi-sba.dz} \\
Phone: +213 660 70 77 96 \\
Portfolio: \href{https://ismail-aissaoui.vercel.app}{ismail-aissaoui.vercel.app}
\end{flushright}

\vspace{1em}

\begin{flushleft}
\textbf{Dr. Moufida Maimour, Dr. Samir Si-Mohammed, Pr. Hind Bril El Haouzi} \\
CRAN Laboratory \\
\textbf{Dr. Malcolm Egan} \\
Inria Equipe Maracas
\end{flushleft}

\vspace{1em}
\noindent\textbf{Subject: Application for PhD Position -- Frugal Data Governance for Digital Twins (PC4)}
\vspace{1em}

\noindent Dear Dr. Maimour, Dr. Si-Mohammed, Pr. Bril El Haouzi, and Dr. Egan,

\vspace{1em}
\noindent
I am highly motivated to apply for the PhD position on Frugal and AI-Enhanced Data Governance for Reliable Digital Twins. As a computer science engineer specializing in Machine Learning and Edge-Optimized architectures, the challenge of shifting from volume-based data logic to information frugality in dynamic cyber-physical systems aligns perfectly with my research trajectory.

\vspace{0.5em}
\noindent
The challenge of feeding digital twins with reliable data under distributed, energy-limited constraints is an issue I confronted extensively during my engineering of the Industrial Gas Turbine Digital Twin. Recognizing that exhaustive telemetry was unsustainable, I designed an Edge-Optimized AI pipeline using Temporal Convolutional Networks (Edge-TCN) to intelligently sample, filter, and compress data directly on constrained edge hardware. This approach allowed for highly accurate anomaly detection using only strictly relevant data streams. I am eager to scale this methodology to address your goals in intelligent sensor selection and robust wireless transmission. Furthermore, through my work in Scientific Machine Learning and GNNs, I have developed robust frameworks to quantify uncertainties and propagate confidence indicators, ensuring that data frugality does not compromise operational reliability.

\vspace{0.5em}
\noindent
I am excited about the opportunity to validate this research on real-world industrial platforms and contribute to the Artemis framework. Please find attached my resume and academic transcripts. I look forward to discussing how my technical competencies align with the CRAN and Inria Maracas laboratories.

\vspace{1.5em}
\noindent
Sincerely, \\[0.5em]
\textbf{Ismail Aissaoui}

\end{document}
