\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}

\hypersetup{colorlinks=true, urlcolor=blue, linkcolor=black}

\begin{document}
\thispagestyle{empty}

\begin{flushright}
\textbf{Ismail Aissaoui} \\
Email: \href{mailto:i.aissaoui@esi-sba.dz}{i.aissaoui@esi-sba.dz} \\
Phone: +213 660 70 77 96 \\
Portfolio: \href{https://ismail-aissaoui.vercel.app}{ismail-aissaoui.vercel.app}
\end{flushright}

\vspace{1em}

\begin{flushleft}
\textbf{Prof. Romain Rouvoy} (University of Lille) \\
\textbf{Dr. Quentin Perez} (INSA Rennes) \\
Spirals \& DiverSE project-teams
\end{flushleft}

\vspace{1em}
\noindent\textbf{Subject: Application for PhD Position -- Improving Sustainability in the Physical-to-Digital Twin Continuum (PC3)}
\vspace{1em}

\noindent Dear Prof. Rouvoy and Dr. Perez,

\vspace{1em}
\noindent
I am writing to express my strong interest in the PC3 PhD position focused on developing a sustainable middleware framework for adaptive digital twin deployment. My proven experience in optimizing complex machine learning architectures for low-power edge hardware makes me an ideal candidate to bridge the physical-to-digital twin continuum while rigorously minimizing environmental and computational footprints.

\vspace{0.5em}
\noindent
My commitment to sustainable AI engineering is best demonstrated by my work on the Industrial Digital Twin (LM2500 Gas Turbine). Rather than relying on cloud-heavy computations which incur massive energy costs, I specialized in Edge-Optimized AI. Specifically, I integrated highly efficient Mamba-SSM sequence models directly onto constrained edge hardware for real-time telemetry processing. By adapting the computation directly to the physical deployment constraints, I significantly reduced the energy requirements of continuous monitoring. This hands-on expertise directly translates to your goal of building an adaptive, eco-conscious middleware capable of dynamically scaling resources across the digital twin continuum based on the current context.

\vspace{0.5em}
\noindent
Furthermore, my background in Software Engineering provides a robust foundation for designing middleware architectures capable of seamlessly operating across heterogeneous hardware---from lightweight IoT sensors up to high-performance computing clusters. I am highly motivated to leverage these skills to build a deployment framework that autonomously optimizes resource usage, ensuring that the digital twin remains highly available and environmentally sustainable. I am excited about the opportunity to contribute to the Artemis platform. Please find attached my resume and academic transcripts. I welcome the opportunity to discuss my application further.

\vspace{1.5em}
\noindent
Sincerely, \\[0.5em]
\textbf{Ismail Aissaoui}

\end{document}
