\documentclass[11pt, a4paper]{letter}
\usepackage[utf8]{inputenc}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}

\begin{document}
\begin{letter}{Admissions Committee \\ Cranfield University \\ Bedford, UK}
\opening{Dear Admissions Committee,}

I am writing to express my strong interest in the PhD position regarding the development and optimization of ultra-efficient and power-dense ice protection systems for future aircraft. As an AI \& Data Science Engineer with deep expertise in thermodynamic modeling and aerospace constraints, I am exceptionally well-prepared for this project.

For my State Engineer thesis, I developed a highly complex "Gas Turbine Digital Twin." This required rigorous modeling of thermodynamic degradation, temperature gradients, and fluid dynamics within high-stress mechanical environments. I engineered hybrid neural architectures (ST-KDFormer, Temporal Convolutional Networks) to predict thermal anomalies while strictly adhering to the laws of energy conservation. Furthermore, my work on Physics-Informed Neural Networks (PI-DeepONet) successfully embedded fluid dynamic equations (0D Windkessel) directly into the neural training loop via PyTorch Autograd.

This exact intersection of computational fluid/thermal dynamics and advanced AI optimization is critical for next-generation ice protection systems. I am highly motivated to apply my digital twin architecture experience to optimize power density, simulate thermal distributions, and design ultra-efficient de-icing control systems for aerospace applications.

I would welcome the opportunity to discuss my Gas Turbine Digital Twin research with you in an interview.

\closing{Sincerely, \\ Ismail Aissaoui \\ \href{https://ismail-aissaoui.vercel.app}{https://ismail-aissaoui.vercel.app}}
\end{letter}
\end{document}