\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}

\hypersetup{colorlinks=true, urlcolor=blue, linkcolor=black}

\begin{document}
\thispagestyle{empty}

\begin{flushright}
\textbf{Ismail Aissaoui} \\
Email: \href{mailto:i.aissaoui@esi-sba.dz}{i.aissaoui@esi-sba.dz} \\
Phone: +213 660 70 77 96 \\
Portfolio: \href{https://ismail-aissaoui.vercel.app}{ismail-aissaoui.vercel.app}
\end{flushright}

\vspace{1em}

\begin{flushleft}
\textbf{Prof. Khalil Drira} (LAAS-CNRS) \\
\textbf{Dr. Christophe Chassot} (LAAS-CNRS) \\
\textbf{Dr. Thierry Monteko} (LAAS-CNRS)
\end{flushleft}

\vspace{1em}
\noindent\textbf{Subject: Application for PhD Position -- Composing and configuring digital twin architectures (PC2)}
\vspace{1em}

\noindent Dear Prof. Drira, Dr. Chassot, and Dr. Monteko,

\vspace{1em}
\noindent
I am applying for the PC2 PhD position focused on "Composing and configuring digital twin architectures to meet user requirements" with great enthusiasm. With a strong engineering background in distributed systems, Quality of Service (QoS) optimization, and Edge-AI architectures, I am highly motivated to address the challenge of dynamically orchestrating digital twin components to satisfy strict performance, energy, and budgetary constraints.

\vspace{0.5em}
\noindent
In my work engineering the Industrial Gas Turbine Digital Twin, I faced the exact trade-offs your research seeks to optimize. Transporting high-frequency telemetry to the cloud for real-time anomaly detection incurred unacceptable latency and energy costs. To resolve this, I orchestrated an Edge-Optimized architecture, deploying lightweight Temporal Convolutional Networks (Edge-TCN) directly onto constrained edge nodes. By pushing computation to the edge, I dynamically balanced the system's QoS requirements (low latency inference) with resource constraints (limited bandwidth and power). This practical experience managing architectural trade-offs positions me perfectly to formalize these configuration strategies. I am eager to leverage my background in multi-objective optimization and Reinforcement Learning to automate the composition of Digital Twins, ensuring they can adapt their topology in real-time to meet shifting user Service Level Agreements (SLAs).

\vspace{0.5em}
\noindent
I am particularly excited to collaborate with the LAAS-CNRS teams to build these autonomic configuration managers. I am confident that my programming proficiency and deep understanding of distributed cyber-physical systems will allow me to contribute directly to the Artemis platform and the broader goals of the EDT program. Please find attached my resume and academic transcripts. I welcome the opportunity to discuss my application further.

\vspace{1.5em}
\noindent
Sincerely, \\[0.5em]
\textbf{Ismail Aissaoui}

\end{document}
