\documentclass[a4paper,11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{geometry}
\geometry{left=1.5cm,right=1.5cm,top=1.2cm,bottom=1.2cm}

\usepackage{lmodern}
\usepackage{xcolor}
\definecolor{titleblue}{RGB}{0,51,140}

\usepackage{hyperref}
\hypersetup{colorlinks=true, urlcolor=titleblue, linkcolor=titleblue}

\usepackage{titlesec}
\usepackage{enumitem}

\pagestyle{empty}

\titleformat{\section}{\color{titleblue}\Large\bfseries\uppercase}{}{0em}{}[\color{titleblue}\titlerule]
\titlespacing\section{0pt}{8pt}{4pt}
\setlist[itemize]{leftmargin=*,topsep=1pt,itemsep=1pt}

\begin{document}

\begin{center}
    {\Huge\bfseries\color{titleblue} AISSAOUI Ismail}\\[4pt]
    {\Large State Engineer in Artificial Intelligence \& Data Science}\\[6pt]
    ismail.aissaoui.pro@gmail.com $|$ +213 660 70 77 96 $|$ Algeria \\
    \href{https://linkedin.com/in/aissaoui-ismail-6a77a92a7}{linkedin.com/in/aissaoui-ismail-6a77a92a7} $|$ \href{https://github.com/i-aissaoui}{github.com/i-aissaoui}
\end{center}

\section{PROFESSIONAL SUMMARY}
State Engineer graduated from ESI-SBA, specializing in distributed architectures, generative surrogates, and metaheuristic optimization. Expert in cyber-physical systems (CPS) and edge-cloud inference for energy systems. PhD candidate focused on Distributed AI for collaborative energy performance.

\section{WORK EXPERIENCE}
\textbf{AI Engineer Intern — Digital Twin & Edge Computing} \hfill Jan 2026 -- Present \\
\textbf{Sonatrach (Pipeline Transport Branch)} \\
\begin{itemize}
    \item Designed a dual Edge/Cloud architecture for industrial gas turbine monitoring.
    \item Achieved \textbf{0.04ms} edge inference latency using \textbf{C++ JIT Compiled xLSTM}.
    \item Developed a generative surrogate based on \textbf{Mamba-SSM} for "What-If" simulations.
    \item Integrated \textbf{Physics-Informed Neural Networks (PINN)} for thermodynamic consistency.
\end{itemize}

\textbf{Network Engineering Intern} \hfill Sep 2024 \\
\textbf{Algérie Télécom RMC Center}

\section{EDUCATION}
\textbf{National School of Computer Science (ESI-SBA, Algeria)} \hfill 2021 -- 2026 \\
\textbf{State Engineer's Degree \& MSc in Artificial Intelligence}

\section{TECHNICAL SKILLS}
\begin{itemize}
    \item \textbf{Distributed AI}: Federated Learning (architecture design), Distributed Inference, Flower.
    \item \textbf{Optimization}: PSO, Genetic Algorithms (GA), ACO, Bayesian Optimization.
    \item \textbf{Deep Learning}: PyTorch, Mamba-SSM, xLSTM, Transformers, GNN, PINN.
    \item \textbf{Stack}: C++, Python (FastAPI), Docker, Kubernetes, MLflow, CUDA, SQL.
\end{itemize}

\section{RESEARCH & ENGINEERING PROJECTS}

\textbf{University Scheduling (NP-Complete Optimization)} \hfill 2025 \\
Automated timetabling system using hybrid metaheuristics (\textbf{PSO/ACO/GA}).
\textit{Key skill: Dynamic optimization under hard constraints.}

\textbf{Aura — Adaptive Reinforcement Learning System} \hfill 2025 \\
Trading platform with distributed real-time data pipelines and DQN agents.

\textbf{Geo-RAG — Geospatial Knowledge Retrieval} \hfill 2025 \\
Intelligent geospatial assistant using RAG and spatial reasoning for decision support.

\textbf{Advanced NLP Optimization} \hfill 2025 \\
Multilingual content moderation optimized via metaheuristic hyperparameter search.

\textbf{Industrial Safety & Tracking (CV)} \hfill 2025 \\
Real-time PPE detection and object tracking in industrial environments (YOLOv8).

\section{LANGUAGES}
Arabic (Native), English (Advanced), French (Fluent).

\end{document}
